% !TEX root = ../main.tex
\begin{abstract}
Current election verification protocols delegate proof validation to independent auditors, treating integrity verification as a secondary manual process. 
We present \textsc{Zeeperio}, a zk-SNARK system that verifies the correctness of election results on the Ethereum blockchain. 
Unlike prior systems that achieve verification through manual audits or off-chain computation, Zeeperio verifies proofs autonomously via smart contracts, allowing all network participants to independently confirm correctness without trusting any third-party intermediaries.
Zeeperio replaces the Eperio protocol's linear-sized proof data with a custom succinct argument where proof size and verification time are constant in the number of ballots. 
We demonstrate that an election with $\mathcal{B}=100,000$ ballots and $\mathcal{C}=5$ candidates verifies on Ethereum L1 for under $\$60 \mathsf{USD}$ (at the time of writing), using the precompiles introduced by EIP 196 and 197.
Compared to recent STARK-based election verification systems, \textsc{Zeeperio} is significantly more practical for blockchain deployment. 
A leading STARK implementation requires proofs of size $\sim3\mathsf{MB}$ for $32,768$ ballots and generates proofs in roughly $9$ days. 
On the other hand, Zeeperio generates proofs of only a few kilobytes for $100,000$ ballots in under $3$ hours on standard hardware. 
This $>100\times$ reduction in proof size directly translates to lower transaction costs and improved on-chain scalability for larger elections.
\end{abstract}