% !TEX root = ../main.tex

\clearpage

\section{Orphaned Text}

Zeeperio shifts from statistical audits to cryptographic arguments of knowledge. 
At a high level, Zeeperio uses the Poly-IOP model to encodes the entire state of an election as a small set of polynomials. 
Instead of writing a generic arithmetic circuit, Zeeperio works directly at the polynomial level to design custom constraints for ballot structure, sums over ballots, and tallies.
Then, using the KZG commitment scheme, Zeeperio allows the Election Authority (EA) to generate a single, succinct proof that the election outcome is correct.
This proof is constant in size and verification time, regardless of how many voters cast their ballots.

This efficiency allows for the verification logic to be encoded into an
Ethereum smart contract. Instead of requiring observers to download data and
run software, the \emph{public audit} becomes a transaction on a the blockchain. 
If the smart contract accepts the proof, the election tally is mathematically guaranteed to be consistent with the committed ballots. 
This lowers the barrier to verification from running complex cryptographic software to checking a simple status flag on the Ethereum block explorer.

\subsection{Threat Model and Contributions}

Before detailing the protocol mechanics, we formalize the operational environment and the specific contributions of this work relative to the state of the art.

\subsection{The RealCryptik Threat Model}
Zeeprio adopts the \textit{RealCryptik} threat model. 
Traditional E2E literature often models the EA as a powerful adversary that must be prevented from learning individual votes at all costs. 
However, this model often ignores the reality of elections. In many scenarios, the EA has the full capability to deanonymize votes.

The RealCryptik model explicitly assumes that the EA \textbf{has access to who voted for whom}. Under this assumption, the primary security goal shifts from absolute privacy to absolute \textbf{integrity}. 
The system must guarantee that even an EA with full view of voter choices cannot manipulate an election without detection. This model reflects the reality of \emph{black box} vendors while enforcing the verification constraints necessary for public trust. 
While public privacy is maintained through zero-knowledge proofs, the protocol also prevents the EA from manipulating the outcome based on their knowledge.

\subsection{Contributions}
This work presents the following contributions.

\begin{description} 
\item \textbf{Succinct universal verification:} All election constraints are encoded as a single Poly-IOP relation and proven via a zkSNARK proof, independent of the number of voters.
\item \textbf{Enhanced privacy and dispute resolution:}
  Confirmation codes are committed to a single polynomial and are only selectively opened when needed.
  After a voter has cast their ballot, they receives a receipt containing a confirmation code to which they can check it appears in the public bulletin board. 
 This is done in a way that prevents the receipt from being used as a proof of how the voter voted.
  \item \textbf{On-chain verification:}
  The final proof is verified by an Ethereum smart contract. This removes the need for a proprietary verifier software and anchors the election result in a public, tamper-evident ledger.
\end{description}




\section{Preliminaries}

We now introduce the cryptographic tools used in Zeeperio.

\subsection{Polynomial interactive oracle proofs}

A polynomial interactive oracle proof (Poly-IOP) is an interactive proof where the prover sends commitments to polynomials and the verifier has oracle access to these polynomials through evaluation queries.
Formally, a Poly-IOP protocol for a relation $\mathcal{R}$ between public input $x$ and witness $w$ follows:
\begin{enumerate}[label=(\roman*)]
  \item The prover, given $x$ and $w$, computes polynomials $f_1,\dots,f_m$ and sends commitments to them.
  \item The verifier sends random challenges $r_1,\dots,r_\ell$.
  \item The prover answers with evaluations $f(r_\ell)$ and proofs of correct evaluation.
  \item The verifier checks the evaluations satisfy a system of polynomial identities and the evaluation proofs are valid.
\end{enumerate}
If all checks pass, the verifier accepts the statement \emph{there exists $w$ such that $(x,w) \in \mathcal{R}$}.

\subsection{KZG polynomial commitments}

Zeeperio uses the KZG (Kate-Zaverucha-Goldberg) polynomial commitment scheme.
We recall its interface at a high level.
A trusted setup is used to produces a structured reference string (SRS) consisting of group elements
\[
  \{g, g^\tau, g^{\tau^2}, \ldots, g^{\tau^d}\} \in G_1, \qquad \{h, h^\tau\} \in G_2,
\]
for a secret $\tau$.

Given a polynomial $f(X) = \sum_{i=0}^d f_i X^i$, the commitment is
\[
  \mathsf{Com}(f) = \sum_{i=0}^d f_i [\tau^i] \in G_1.
\]
To open $\mathsf{Com}(f)$ at a point $z \in \mathbb{F}$, the prover computes $y = f(z)$ and the quotient
\[
  q(X) = \frac{f(X) - y}{X - z}
\]
and returns an opening proof $\pi = \mathsf{Com}(q)$.
The verifier checks that
\[
  e(\mathsf{Com}(f) - y, h) = e(\pi, [h^\tau - z]),
\]
where $e : G_1 \times G_2 \to G_T$ is a bilinear pairing.

In Zeeperio we use KZG both to commit to the election polynomials.
We combine multiple constraints into a single quotient polynomial using random coefficients and prove that it vanishes on $\Omega$ by checking a single evaluation.

\subsection{Zero-knowledge and Fiat--Shamir}

We can apply the Fiat-Shamir heuristic to the Poly-IOP to make the protcol non-interactive.
This can be done by replacing the verifier's random challenges by outputs of a hash function on the transcript.
To achieve zero-knowledge, we add random blinding polynomials to all witness polynomials before committing, and we ensure that any information opened to the verifier is public.
Therefore, the only meaningful information revealed by the proof is that the constraints are satisfied, while keeping the underlying ballot structure and confirmation codes hidden.

\subsection{Ethereum verification model}

Finally, we briefly outline the on-chain verification model.
Ethereum provides precompiled contracts for the BN254 pairing and scalar multiplication.
The verification contract uses the SRS and the structure of the combined pairing equation corresponding to the KZG openings.
Given the public input and the proof, the contract performs a simple pairing check.
If the check passes, the election result has been cryptographically verified.

\section{The Zeeperio Protocol}

\paragraph{Election data and domain.}
We consider an election with $\mathcal{B}$ ballots and $\mathcal{C}$ candidates, with $\mathcal{P}=\mathcal{B}\cdot \mathcal{C}$ ballot-candidate positions listed in canonical order. 
Let $i=j\cdot \mathcal{C}+k$ for ballot index $j\in\{0,\dots,\mathcal{B}-1\}$ and candidate index $k\in\{0,\dots,\mathcal{C}-1\}$. 
The EA forms the following columns, each of length $\mathcal{P}$.
\begin{enumerate}
    \item \textbf{Ballot Column ($\mathsf{B_{ID}}$):} Identifies the unique ballot $\mathcal{B}_j$.
    \item \textbf{Confirmation Code Column ($\mathsf{C}_\text{confirm}$):} A unique confirmation code issued to each position. The voter receives the code corresponding to their selection.
    \item \textbf{Mark Column ($\mathsf{M_{ark}}$):} Indicates if the position was selected for vote.
    \item \textbf{Audit Column ($\mathsf{A_{udit}}$):} Indicates if the ballot $\mathcal{B}_j$ was selected for audit.
\end{enumerate}

For efficient FFT operations, we require an evaluation domain size $n$ that is a power of two. 
We set $n = 2^t$ where $t = \lceil \log_2 \mathcal{P} \rceil$. 
The EA pads the columns with zeros for indices $i$ where $\mathcal{P} \le i < n$. 
The columns $\mathsf{M_{ark}}$ and $\mathsf{C}_{\mathsf{confirm}}$ are witness data and are not published. 

Let $\mathbb{F}$ be the prime field used by the commitment scheme and let $\Omega=\{\omega^0,\dots,\omega^{n-1}\}$
be an evaluation domain with primitive $n$th root $\omega$. Each column is interpolated into a polynomial
$F(X)\in \mathbb{F}[X]_{<n}$ satisfying $F(\omega^i)=F[i]$ on $\Omega$.

\paragraph{Commitments and Fiat-Shamir.}
Zeeperio bases itself as a Poly-IOP using the KZG polynomial commitments with
$\mathsf{KZG.Commit}(F)$, $\mathsf{KZG.Open}(F,z)$, and $\mathsf{KZG.Verify}(C,z,y,\pi)$, and derives all verifier challenges via Fiat-Shamir.  

\paragraph{Zero-knowledge.}
We use the hiding variant of KZG commitments (commit as $g^{F(\tau)}h^r$), and
off-domain masking (randomize $F'(X)=F(X)+\rho\cdot Z_H(X)$ where $Z_H(X)=X^n-1$ vanishes on $\Omega$),
so commitments and openings do not leak vote or receipt information.  

\subsection{Setup}
In the setup phase, the EA performs the following steps.
\begin{enumerate}[label=(S\arabic*)]
  \item Obtains KZG SRS from a publicly run Ethereum Powers-of-Tau ceremony $\mathsf{SRS}=(g,g^\tau,g^{\tau^2},\dots,g^{\tau^d})$, supporting degree $\le d$ commitments. 
  \item Fixes the finite field $\mathbb{F}_q$, root-of-unity domain $\Omega$ of size $n$, and encoding of election data into polynomials.
  \item Generates a set of unique confirmation codes and assigns each $\mathsf{C}_confirm$ code to each position on the ballot.
  \item Deploys an Ethereum smart contract that uses the SRS and the verification logic for the Zeeperio proof.
\end{enumerate}
The protocol uses a universal SRS from a Powers-of-Tau ceremony,
 

\subsection{Main Election Proof}
\paragraph{Goal.}
The EA proves in zero-knowledge that the committed election columns satisfy:
\begin{itemize}
\item well-formed audit marks
\item well-formed cast marks
\item audit/mark exclusion
\item published tally is consistent with the mark column
\end{itemize}


\paragraph{Constraint family as vanishing checks.}
We define a family of low-degree polynomials $\{P_i(X)\}$ such that the election is valid iff
\begin{equation*}
P_i(\omega^t)=0 \quad \forall \omega^t\in\Omega \text{ and for all } i.
\end{equation*}
These constraints encode the following, each as a polynomial identity that vanishes on $\Omega$:

\noindent\textbf{Audit column $\mathsf{A_{udit}}$:}
\begin{enumerate}
  \item The padded values must be set to $\mathsf{A_{udit}}[i]=0$ for $i\ge P$.
  \item All values should either be set to 1, or 0 $\mathsf{A_{udit}}[i]\in\{0,1\}$.
  \item For each ballot $j$, the $\mathcal{C}$ entries $\mathsf{A_{udit}}[j\mathcal{C}],\dots,\mathsf{A_{udit}}[j\mathcal{C}+\mathcal{C}-1]$ are equal.
  Additionally, the block-sum for each $\mathsf{A_{udit}}$ block is $\in\{0,C\}$.
  \item The number of 1s in $\mathsf{A_{udit}}$ is equal to the published number of audited ballots $\mathsf{Sum_A}\cdot \mathcal{C}$ using an accumulator constraint.
\end{enumerate}

\noindent\textbf{Mark column $\mathsf{M_{ark}}$:}
\begin{enumerate}
  \item The padded values must be set to $\mathsf{M_{ark}}[i]=0$ for $i\ge P$.
  \item All values should either be set to 1, or 0 $\mathsf{M_{ark}}[i]\in\{0,1\}$.
  \item The block-sum for each $\mathsf{M_{ark}}$ block is $\in\{0,C\}$.
  \item The total number of marks is equal to the published number of ballots cast $\mathsf{Sum_M}$, enforcing one mark per cast ballot using an accumulator.
\end{enumerate}

\noindent\textbf{Audit and Mark Exclusion:}
No ballot must be both audited and cast $\mathsf{A_{udit}}[i]\cdot \mathsf{M_{ark}}[i]=0$ for all $i < n$.

\noindent\textbf{Tally correctness:}
For each candidate $c\in\{0,\dots,\mathcal{C}-1\}$, the published tally $\mathsf{Sum}_c$ is equal to the sum of $\mathsf{M_{ark}}[i]$ over the
stream $\{c, c+\mathcal{C}, c+2\mathcal{C},\dots\}$, enforced by a strided accumulator (shift by $\omega^\mathcal{C}$) with boundary conditions
for the first/last stream elements.

\paragraph{Batched quotient argument.}
Let $k=17+\mathcal{C}$ be the number of vanishing polynomials. 
Using Fiat-Shamir, derive $\alpha \stackrel{\$}{\leftarrow} \mathbb{F}$ and define the batched vanishing polynomial
\begin{equation*}
P_{\mathsf{vanish}}(X)=\sum_{i=1}^{k}\alpha^{i-1}\,P_i(X).
\end{equation*}

Then form the quotient
\[
Q(X)=\frac{P_{\mathsf{vanish}}(X)}{Z_H(X)} \quad \text{where } Z_H(X)=X^n-1.
\]
If all constraints hold on $\Omega$, $Q(X)$ exists as a polynomial.  

\paragraph{Proof.}
The EA commits to the masked witness and auxiliary polynomials required by the constraints
($\mathsf{A_{udit}},\mathsf{M_{ark}}$ and the block-sum/accumulator polynomials) and to $Q$,
then opens them at a single Fiat-Shamir point $\zeta\in\mathbb{F}$.  

\paragraph{Verification.}
From the opened values at $\zeta$, the verifier reconstructs $P_{\mathsf{vanish}}(\zeta)$ and checks
\begin{equation*}
P_{\mathsf{van}}(\zeta) \stackrel{?}{=} Q(\zeta)\cdot(\zeta^n-1),
\end{equation*}
accepting iff the check passes under $\mathsf{KZG.Verify}$.  

\subsection{Voter Verification Proofs}
Voter verification is a \emph{separate} zero-knowledge proof from the main election proof, but it reuses the same setup and the same committed election polynomials.  

\paragraph{Print audit (spoiled ballots).}
Given a spoiled ballot $\mathcal{B}_j$, the EA opens the commitments for the corresponding index block $\{j\mathcal{C},\dots,j\mathcal{C}+\mathcal{C}-1\}$ to show the ballot was audited and not cast.
There is no need to satisfy the receipt-freeness requirement for audited ballots.

\paragraph{Ballot inclusion (receipt check without revealing the choice).}
To show a voter’s receipt code corresponds to a marked position without revealing which candidate was marked, the EA proves a permutation relation over tuples.
For each $i$, form $(b_i,c_i,m_i)=(\mathsf{B_{ID}}[i],\mathsf{C}_{\mathsf{confirm}}[i],\mathsf{M_{ark}}[i])$ and a shuffled copy
$(b'_i,c'_i,m'_i)=(b_{\sigma(i)},c_{\sigma(i)},m_{\sigma(i)})$ for a secret shuffle $\sigma$.
Using Fiat-Shamir, sample $\alpha,r\stackrel{\$}{\leftarrow} \mathbb{F}$, encode tuples into scalars
$v_i=b_i+\alpha c_i+\alpha^2 m_i$ and $v'_i=b'_i+\alpha c'_i+\alpha^2 m'_i$, define
$V_1[i]=r-v_i$ and $V_2[i]=r-v'_i$, and enforce multiset equality via a grand product accumulator argument.
All resulting checks are expressed as a small set of vanishing polynomials, batched with
a random $\beta$, and verified with a single quotient test exactly as in the main proof.  

After the permutation proof, the EA reveals the $mathcal{C}$ tuples in the shuffled list whose ballot ID equals $\mathcal{B}_j$ via $\mathsf{KZG.Open}$.
Exactly one tuple has $m'=1$, establishing inclusion while the shuffle hides which candidate position was marked.

\paragraph{Receipt correctness (prove a disputed code is \emph{not} on ballot $\mathcal{B}_j$).}
Let the disputed code be $C$. The EA defines a helper indicator polynomial $D(X)$ whose evaluations satisfy
$D(\omega^i)=1$ iff $\mathsf{C}_{\mathsf{confirm}}[i]=C$ using \emph{Fermat's Little Theorem}.
Let $\mathsf{Sel}_j(X)$ be the public selector that is $1$ on indices $\{j\mathcal{C},\dots,j\mathcal{C}+\mathcal{C}-1\}$ and $0$ elsewhere.
The EA proves
\[
z \;=\; \sum_{i=0}^{n-1}\mathsf{Sel}_j(\omega^i)\cdot D(\omega^i) \;=\; 0.
\]
This implies no confirmation code on ballot $\mathcal{B}_j$ is equal to the disputed code $C$ without revealing any of the ballot’s codes.

\section{Security Analysis}

\subsection{Completeness}

\begin{theorem}[Completeness]
    If an honest Prover $\mathcal{P}$ computes the accumulators $Acc_{T_1}(X)$ and $Acc_{T_2}(X)$ according to the backward accumulation rule defined in the protocol, then the Verifier $\mathcal{V}$ accepts with probability 1.
\end{theorem}

\begin{proof}
    The honest prover constructs the backward accumulator such that $Acc_{T_1}(\omega^i) = \prod_{j=i}^{n-1} T_1(\omega^j)$. The protocol enforces constraints via a batched vanishing polynomial $P_{vanish}(X)$.
    \begin{enumerate}
        \item \textbf{Boundary Consistency:} At the last element $X = \omega^{n-1}$, the accumulator is defined as $Acc_{T_1}(\omega^{n-1}) = T_1(\omega^{n-1})$. Consequently, the term $(Acc_{T_1}(X) - T_1(X))$ is zero at this point, satisfying the boundary constraint $P_{vanish1}$.
        \item \textbf{Recursive Consistency:} For all $X \in \Omega$ except $X=\omega^{n-1}$, the recursive definition holds: $Acc_{T_1}(\omega^i) = T_1(\omega^i) \cdot Acc_{T_1}(\omega^{i+1})$. This ensures the constraint $P_{vanish3}$ evaluates to zero on the relevant domain.
        \item \textbf{Product Equality:} Since the tuples are permutations, the total products over $\Omega$ are equal. Thus, $Acc_{T_1}(1) = \prod_{x \in \Omega} T_1(x) = \prod_{x \in \Omega} T_2(x) = Acc_{T_2}(1)$, satisfying the equality constraint $P_{vanish5}$.
    \end{enumerate}
    Since all individual constraint polynomials vanish on $\Omega$, $P_{vanish}(X)$ is divisible by the vanishing polynomial $Z_H(X) = X^n - 1$. Therefore, the quotient check $P_{vanish}(\zeta) - Q(\zeta)Z_H(\zeta) \stackrel{?}{=} 0$ holds for any $\zeta \in \mathbb{F}_q$.
    \qed
\end{proof}

\subsection{Knowledge Soundness}

\begin{theorem}[Knowledge Soundness]
    The protocol satisfies knowledge soundness in the Algebraic Group Model. If a malicious prover ${\mathcal{P}}$ convinces $\mathcal{V}$ with non-negligible probability $\epsilon$, there exists an efficient Extractor $\mathcal{E}$ that outputs polynomials $T(X)$ and $T'(X)$ such that the set of their evaluations on $\Omega$ are permutations of each other.
\end{theorem}

\begin{proof}
    In the AGM, the Extractor $\mathcal{E}$ observes the commitments sent by ${\mathcal{P}}$. Since ${\mathcal{P}}$ outputs valid commitments $[Acc_{T_1}], [Acc_{T_2}]$, it must know the underlying polynomials.
    
    If $\mathcal{V}$ accepts, the equation $P_{vanish}(\zeta) = 0$ holds at a random challenge $\zeta \leftarrow \mathbb{F}_q$. By the Schwartz-Zippel Lemma, this implies that $P_{vanish}(X)$ is divisible by $Z_H(X)$ with overwhelming probability. 
    We unroll these constraints to prove the validity of the statement:

    \begin{enumerate}
        \item \textbf{Unrolling the Accumulator:}
        From the boundary constraint ($P_{vanish1} \equiv 0$), we have $Acc_{T_1}(\omega^{n-1}) = T_1(\omega^{n-1})$.
        From the constraint ($P_{vanish3} \equiv 0$), for any $x \in \Omega$ except $X= \omega^{n-1}$, $Acc_{T_1}(x) = T_1(x) \cdot Acc_{T_1}(\omega x)$.
        With this backwards accumulation, we determine that $Acc_{T_1}(1)$ stores the complete product:
        \begin{equation}
            Acc_{T_1}(1) = \prod_{i=0}^{n-1} T_1(\omega^i)
        \end{equation}
        Similarly, we derive $Acc_{T_2}(1) = \prod_{i=0}^{n-1} T_2(\omega^i)$.

        \item \textbf{Equality of Multisets:}
        The final constraint ($P_{vanish5} \equiv 0$) ensures $Acc_{T_1}(1) = Acc_{T_2}(1)$. Substituting the definitions of $T_1$ and $T_2$:
        \begin{equation}
            \prod_{x \in \Omega} (r - T(x)) = \prod_{x \in \Omega} (r - T'(x))
        \end{equation}
        This equation implies equality between two polynomials in the variable $r$. Since $r$ is chosen uniformly at random by the verifier \emph{after} the commitments to $T(X)$ and $T'(X)$, the equality holds identically with overwhelming probability. 
        Therefore, these polynomials are considered to be \emph{set equal}. Thus, $T'$ is a valid permutation of $T$.
    \end{enumerate}
    \qed
\end{proof}

\subsection{Honest-Verifier Zero-Knowledge}

\begin{theorem}[HVZK]
    The protocol is Honest-Verifier Zero-Knowledge. There exists a Simulator $\mathcal{S}$ that outputs a transcript indistinguishable from a real prover's trace.
\end{theorem}

\begin{proof}
   The Simulator $\mathcal{S}$ operates as follows:

\begin{enumerate}
    \item \textbf{Challenge Sampling:} $\mathcal{S}$ samples random challenges $r, \beta, \zeta \leftarrow \mathbb{F}_q$ exactly as the honest verifier would.
    
    \item \textbf{Simulate Commitments:} $\mathcal{S}$ outputs random group elements for $[Acc_{T_1}], [Acc_{T_2}], [T_1], [T_2]$. Due to the hiding property of KZG (with blinding), these are indistinguishable from real commitments.
    
    \item \textbf{Simulate Evaluations:}
    \begin{itemize}
        \item $\mathcal{S}$ chooses random values for evaluations $\bar{T}_1, \bar{T}_2, \overline{Acc}_{T_1}, \overline{Acc}_{T_2}$ at $\zeta$ and required shifted points (e.g., $\omega\zeta$). This is valid because the blinded polynomials act as One-Time Pads at any point $\zeta \notin \Omega$.
        
        \item $\mathcal{S}$ must ensure the verification equation holds: $P_{vanish}(\zeta) - Q(\zeta)Z_H(\zeta) = 0$.
        
        \item $\mathcal{S}$ computes the value of $P_{vanish}(\zeta)$ using the randomly sampled evaluations and the formulas for $Z_1, Z_2, Z_3$ evaluated at $\zeta$.
        
        \item $\mathcal{S}$ then \textit{sets} the evaluation of the quotient polynomial $\bar{Q} = Q(\zeta)$ specifically to satisfy the equation:
        \[
        \bar{Q} = \frac{P_{vanish}(\zeta)}{Z_H(\zeta)}
        \]
        Since $\zeta$ is random, $Z_H(\zeta) \neq 0$, making this division valid.
    \end{itemize}
    
    \item \textbf{Transcript Consistency:} The tuple of commitments, challenges, and evaluations $(\dots, \bar{Q})$ satisfies the algebraic verification check by construction. Because the evaluations of blinded polynomials are uniformly distributed, the simulated transcript is statistically indistinguishable from a real transcript. 
\end{enumerate}
\end{proof}

\section{Implementation}

\section{Future Work}

We conclude with several directions for extending and deploying Zeeperio.

\paragraph{Integration with optical scanners}

\paragraph{Online voting}
