% !TEX root = ../main.tex

\clearpage


\section{Voatz}
Voatz is a controversial \textbf{mobile voting application} that was used in a few U.S. pilot elections for overseas and military voters between 2018-2020 \cite{voatz-mobile-voting-2020}. 
Unlike the academic protocols discussed above, Voatz is a proprietary system that claimed to offer security and immutability through the \emph{blockchain}, but independent analyses found it lacked E2E verifiability and was severely insecure.
Voatz's front-end is a smartphone app that allows voters to submit ballots electronically.
It advertises features like \emph{blockchain-backed receipts}, \emph{biometrics for authentication}, and \emph{E2E encryption} of ballots.
However, a 2020 security analysis by Specter et al. (MIT) and the cybersecurity firm Trail of Bits found that it lacked E2E verifiability and contained severe, exploitable security vulnerabilities \cite{specter2020ballot,guido2020our}.

\subsubsection{Verifiability}
Voatz provides no mechanism for voters to independently verify if the app had recorded their choices correctly.
There is no public bulletin board or tracking number a voter can check. 
Voters have to trust the Voatz servers entirely, thereby failing to achieve \emph{cast-as-intended} verifiability.
Similarly, voters have no way to confirm their ballot is included unaltered in the tally as Voatz does not publish anonymized receipts or a public list of votes, thereby failing to achieve \emph{recorded-as-cast} verifiability.
Finally, none of the tallying is provably transparent as the backend is effectively a black box, thereby failing to achieve \emph{counted-as-collected} verifiability.
As the analysts from Trail of Bits put it, Voatz "provides no meaningful end-to-end verification" and offers neither individual nor universal verifiability in a formal sense \cite{trailofbits-voatz-2020}.


\subsubsection{Security Vulnerabilities}
Another concern the researchers found was the Voatz app and infrastructure had multiple vulnerabilities. 
For example, an attacker with root access on the voter's phone could intercept and alter the voter's choices before they are sent, and the Voatz app's checking mechanism could be easily evaded. 
The network protocol was also found to potentially leak information about the vote, and since the blockchain was run privately by Voatz's servers, it did not protect against a server-side attack altering votes \cite{statescoop-voatz-audit-2020}. 
Basically, Voatz's \emph{blockchain} is a permissioned ledger with no public auditability.
Only Voatz and its partners have nodes, so it functions like a centralized database. 

The advantage of blockchain is that it is tamper-evident, but because outsiders cannot observe the chain directly, and the system lacks independent auditing channels, the supposed \emph{publicly verifiable} blockchain functions as a \emph{black box}. 
The MIT analysis concluded that there were "numerous vulnerabilities [that] allow different kinds of adversaries to alter, stop, or expose a user's vote" \cite{specter2020ballot}. 
This included the possibility of some malware on the phone or a malicious Wi-Fi network that could change votes undetected, or that insiders could corrupt the blockchain records without voters or observers noticing \cite{govtech-voatz-audit-2020}.

\subsubsection{Privacy}
In theory, Voatz uses encryption to protect ballot content, but the MIT researchers found ways that an attacker could still learn a voter's choices. 
One example given was that with root access, an attacker could \emph{bypass defenses} and learn the user's vote \cite{statescoop-voatz-audit-2020}. 
Thus, Voatz failed to guarantee \emph{ballot secrecy} against realistic threats. 
As for \emph{coercion-resistance} or \emph{receipt freeness} verifiability, Voatz actually provided voters with a receipt of sorts (the app would indicate that the vote was recorded on the blockchain). 
However, because the process was not transparent, this receipt was not independently verifiable by a third party.
A voter under coercion could potentially show their app screen or a confirmation message, but the coercer would have to trust Voatz's confirmation itself. 
Regardless, since the system itself was insecure, discussing coercion-resistance is almost pointless as one could argue it is \emph{trivially receipt free} because even the voter cannot prove their vote to an outsider (as nothing publicly verifiable is produced). 
However, the lack of any mechanism to change or invalidate a coerced vote, or to provide a fake proof means if an attacker compromised the device, the voter had no recourse. 

\subsubsection{Trust Model}
Voatz expects users to completely trust the vendor's infrastructure, which in this case is the app, the cloud servers, and the private blockchain.
In Voatz, if the company's servers said a vote was counted, the voter has to believe it without independent evidence. 
This is the antithesis of E2E verifiability, which aims to remove the need for such trust. 
The MIT researchers also noted Voatz's \emph{lack of transparency}, and \emph{closed-source} code as criticial weaknesses.
While Voatz claimed to conduct bug bounty programs and security audits, these were primarily \emph{black box} tests until the Trail of Bits assessment \cite{voatz-audits}.
Even after the assesment identified critical vulnerabilities, Voatz disputed many findings and continued operations, raising concerns about the company's responsiveness to independent, security research \cite{techtarget-voatz-mit-2020}.


\subsubsection{Deployment}
Voatz was used in a very limited way. 
For example, West Virginia's 2018 midterm elections allowed overseas military from certain counties to vote via Voatz, and some jurisdictions (parts of Utah in 2020, and a few small municipal pilots) experimented with it as well \cite{moore-sawhney-wv-mobile-voting-2019}. 
The usage was very narrow, where there were tens of voters in some cases. 
These pilots were met with \emph{intense} scrutiny and criticism from the security community. 
After the public disclosure of Voatz's vulnerabilities and a DHS security audit, West Virginia and others backed away from the app. 
The takeaway is that Voatz is \textbf{not} an E2E-V protocol at all, despite its marketing suggestions. 
It is essentially a conventional internet voting system with an attached marketing buzzword, \emph{blockchain}.
Voatz shows us that simply using buzzwords like \emph{blockchain} or \emph{encryption} does not guarantee security or verifiability. 
Without open, independent verifiability and rigorous peer review, a voting system cannot be trusted. 
Voatz has since become a cautionary tale, demonstrating that \emph{security through obscurity} and \emph{lack of transparency} are unacceptable in voting systems. 
Various computer and election security research communities have extensively criticized Voatz's approach, with multiple independent analyses identifying critical vulnerabilities. 
The consensus among academic security researchers is that it fails to meet basic requirements for secure, verifiable elections.


\section{Orphaned Text}

Zeeperio shifts from statistical audits to cryptographic arguments of knowledge. 
At a high level, Zeeperio uses the PIOP model to encodes the entire state of an election as a small set of polynomials. 
Instead of writing a generic arithmetic circuit, Zeeperio works directly at the polynomial level to design custom constraints for ballot structure, sums over ballots, and tallies.
Then, using the KZG commitment scheme, Zeeperio allows the Election Authority (EA) to generate a single, succinct proof that the election outcome is correct.
This proof is constant in size and verification time, regardless of how many voters cast their ballots.

This efficiency allows for the verification logic to be encoded into an
Ethereum smart contract. Instead of requiring observers to download data and
run software, the \emph{public audit} becomes a transaction on a the blockchain. 
If the smart contract accepts the proof, the election tally is mathematically guaranteed to be consistent with the committed ballots. 
This lowers the barrier to verification from running complex cryptographic software to checking a simple status flag on the Ethereum block explorer.

\subsection{Threat Model and Contributions}

Before detailing the protocol mechanics, we formalize the operational environment and the specific contributions of this work relative to the state of the art.

\subsection{The Realcryptik Threat Model}
Zeeprio adopts the \textit{realcryptik} threat model. 
Traditional E2E literature often models the EA as a powerful adversary that must be prevented from learning individual votes at all costs. 
However, this model often ignores the reality of elections. In many scenarios, the EA has the full capability to deanonymize votes.

The realcryptik model explicitly assumes that the EA \textbf{has access to who voted for whom}. Under this assumption, the primary security goal shifts from absolute privacy to absolute \textbf{integrity}. 
The system must guarantee that even an EA with full view of voter choices cannot manipulate an election without detection. This model reflects the reality of \emph{black box} vendors while enforcing the verification constraints necessary for public trust. 
While public privacy is maintained through zero-knowledge proofs, the protocol also prevents the EA from manipulating the outcome based on their knowledge.

\subsection{Contributions}
This work presents the following contributions.

\begin{description} 
\item \textbf{Succinct universal verification:} All election constraints are encoded as a single PIOP relation and proven via a zkSNARK proof, independent of the number of voters.
\item \textbf{Enhanced privacy and dispute resolution:}
  Confirmation codes are committed to a single polynomial and are only selectively opened when needed.
  After a voter has cast their ballot, they receives a receipt containing a confirmation code to which they can check it appears in the public bulletin board. 
 This is done in a way that prevents the receipt from being used as a proof of how the voter voted.
  \item \textbf{On-chain verification:}
  The final proof is verified by an Ethereum smart contract. This removes the need for a proprietary verifier software and anchors the election result in a public, tamper-evident ledger.
\end{description}




\section{Preliminaries}

We now introduce the cryptographic tools used in Zeeperio.

\subsection{Polynomial interactive oracle proofs}

A polynomial interactive oracle proof (PIOP) is an interactive proof where the prover sends commitments to polynomials and the verifier has oracle access to these polynomials through evaluation queries.
Formally, a PIOP protocol for a relation $\mathcal{R}$ between public input $x$ and witness $w$ follows:
\begin{enumerate}[label=(\roman*)]
  \item The prover, given $x$ and $w$, computes polynomials $f_1,\dots,f_m$ and sends commitments to them.
  \item The verifier sends random challenges $r_1,\dots,r_\ell$.
  \item The prover answers with evaluations $f(r_\ell)$ and proofs of correct evaluation.
  \item The verifier checks the evaluations satisfy a system of polynomial identities and the evaluation proofs are valid.
\end{enumerate}
If all checks pass, the verifier accepts the statement \emph{there exists $w$ such that $(x,w) \in \mathcal{R}$}.

\subsection{KZG polynomial commitments}

Zeeperio uses the KZG (Kate-Zaverucha-Goldberg) polynomial commitment scheme.
We recall its interface at a high level.
A trusted setup is used to produces a structured reference string (SRS) consisting of group elements
\[
  \{g, g^\tau, g^{\tau^2}, \ldots, g^{\tau^d}\} \in G_1, \qquad \{h, h^\tau\} \in G_2,
\]
for a secret $\tau$.

Given a polynomial $f(X) = \sum_{i=0}^d f_i X^i$, the commitment is
\[
  \mathsf{Com}(f) = \sum_{i=0}^d f_i [\tau^i] \in G_1.
\]
To open $\mathsf{Com}(f)$ at a point $z \in \mathbb{F}$, the prover computes $y = f(z)$ and the quotient
\[
  q(X) = \frac{f(X) - y}{X - z}
\]
and returns an opening proof $\pi = \mathsf{Com}(q)$.
The verifier checks that
\[
  e(\mathsf{Com}(f) - y, h) = e(\pi, [h^\tau - z]),
\]
where $e : G_1 \times G_2 \to G_T$ is a bilinear pairing.

In Zeeperio we use KZG both to commit to the election polynomials.
We combine multiple constraints into a single quotient polynomial using random coefficients and prove that it vanishes on $\Omega$ by checking a single evaluation.

\subsection{Zero-knowledge and Fiat--Shamir}

We can apply the Fiat-Shamir heuristic to the PIOP to make the protcol non-interactive.
This can be done by replacing the verifier's random challenges by outputs of a hash function on the transcript.
To achieve zero-knowledge, we add random blinding polynomials to all witness polynomials before committing, and we ensure that any information opened to the verifier is public.
Therefore, the only meaningful information revealed by the proof is that the constraints are satisfied, while keeping the underlying ballot structure and confirmation codes hidden.

\subsection{Ethereum verification model}

Finally, we briefly outline the on-chain verification model.
Ethereum provides precompiled contracts for the BN254 pairing and scalar multiplication.
The verification contract uses the SRS and the structure of the combined pairing equation corresponding to the KZG openings.
Given the public input and the proof, the contract performs a simple pairing check.
If the check passes, the election result has been cryptographically verified.

\section{The Zeeperio Protocol}

\paragraph{Election data and domain.}
We consider an election with $\mathcal{B}$ ballots and $\mathcal{C}$ candidates, with $\mathcal{P}=\mathcal{B}\cdot \mathcal{C}$ ballot-candidate positions listed in canonical order. 
Let $i=j\cdot \mathcal{C}+k$ for ballot index $j\in\{0,\dots,\mathcal{B}-1\}$ and candidate index $k\in\{0,\dots,\mathcal{C}-1\}$. 
The EA forms the following columns, each of length $\mathcal{P}$.
\begin{enumerate}
    \item \textbf{Ballot Column ($\mathsf{B_{ID}}$):} Identifies the unique ballot $\mathcal{B}_j$.
    \item \textbf{Confirmation Code Column ($\mathsf{C}_\text{confirm}$):} A unique confirmation code issued to each position. The voter receives the code corresponding to their selection.
    \item \textbf{Mark Column ($\mathsf{M_{ark}}$):} Indicates if the position was selected for vote.
    \item \textbf{Audit Column ($\mathsf{A_{udit}}$):} Indicates if the ballot $\mathcal{B}_j$ was selected for audit.
\end{enumerate}

For efficient FFT operations, we require an evaluation domain size $n$ that is a power of two. 
We set $n = 2^t$ where $t = \lceil \log_2 \mathcal{P} \rceil$. 
The EA pads the columns with zeros for indices $i$ where $\mathcal{P} \le i < n$. 
The columns $\mathsf{M_{ark}}$ and $\mathsf{C}_{\mathsf{confirm}}$ are witness data and are not published. 

Let $\mathbb{F}$ be the prime field used by the commitment scheme and let $\Omega=\{\omega^0,\dots,\omega^{n-1}\}$
be an evaluation domain with primitive $n$th root $\omega$. Each column is interpolated into a polynomial
$F(X)\in \mathbb{F}[X]_{<n}$ satisfying $F(\omega^i)=F[i]$ on $\Omega$.

\paragraph{Commitments and Fiat-Shamir.}
Zeeperio bases itself as a PIOP using the KZG polynomial commitments with
$\mathsf{KZG.Commit}(F)$, $\mathsf{KZG.Open}(F,z)$, and $\mathsf{KZG.Verify}(C,z,y,\pi)$, and derives all verifier challenges via Fiat-Shamir.  

\paragraph{Zero-knowledge.}
We use the hiding variant of KZG commitments (commit as $g^{F(\tau)}h^r$), and
off-domain masking (randomize $F'(X)=F(X)+\rho\cdot Z_H(X)$ where $Z_H(X)=X^n-1$ vanishes on $\Omega$),
so commitments and openings do not leak vote or receipt information.  

\subsection{Setup}
In the setup phase, the EA performs the following steps.
\begin{enumerate}[label=(S\arabic*)]
  \item Obtains KZG SRS from a publicly run Ethereum Powers-of-Tau ceremony $\mathsf{SRS}=(g,g^\tau,g^{\tau^2},\dots,g^{\tau^d})$, supporting degree $\le d$ commitments. 
  \item Fixes the finite field $\mathbb{F}_q$, root-of-unity domain $\Omega$ of size $n$, and encoding of election data into polynomials.
  \item Generates a set of unique confirmation codes and assigns each $\mathsf{C}_confirm$ code to each position on the ballot.
  \item Deploys an Ethereum smart contract that uses the SRS and the verification logic for the Zeeperio proof.
\end{enumerate}
The protocol uses a universal SRS from a Powers-of-Tau ceremony,
 

\subsection{Main Election Proof}
\paragraph{Goal.}
The EA proves in zero-knowledge that the committed election columns satisfy:
\begin{itemize}
\item well-formed audit marks
\item well-formed cast marks
\item audit/mark exclusion
\item published tally is consistent with the mark column
\end{itemize}


\paragraph{Constraint family as vanishing checks.}
We define a family of low-degree polynomials $\{P_i(X)\}$ such that the election is valid iff
\begin{equation*}
P_i(\omega^t)=0 \quad \forall \omega^t\in\Omega \text{ and for all } i.
\end{equation*}
These constraints encode the following, each as a polynomial identity that vanishes on $\Omega$:

\noindent\textbf{Audit column $\mathsf{A_{udit}}$:}
\begin{enumerate}
  \item The padded values must be set to $\mathsf{A_{udit}}[i]=0$ for $i\ge P$.
  \item All values should either be set to 1, or 0 $\mathsf{A_{udit}}[i]\in\{0,1\}$.
  \item For each ballot $j$, the $\mathcal{C}$ entries $\mathsf{A_{udit}}[j\mathcal{C}],\dots,\mathsf{A_{udit}}[j\mathcal{C}+\mathcal{C}-1]$ are equal.
  Additionally, the block-sum for each $\mathsf{A_{udit}}$ block is $\in\{0,C\}$.
  \item The number of 1s in $\mathsf{A_{udit}}$ is equal to the published number of audited ballots $\mathsf{Sum_A}\cdot \mathcal{C}$ using an accumulator constraint.
\end{enumerate}

\noindent\textbf{Mark column $\mathsf{M_{ark}}$:}
\begin{enumerate}
  \item The padded values must be set to $\mathsf{M_{ark}}[i]=0$ for $i\ge P$.
  \item All values should either be set to 1, or 0 $\mathsf{M_{ark}}[i]\in\{0,1\}$.
  \item The block-sum for each $\mathsf{M_{ark}}$ block is $\in\{0,C\}$.
  \item The total number of marks is equal to the published number of ballots cast $\mathsf{Sum_M}$, enforcing one mark per cast ballot using an accumulator.
\end{enumerate}

\noindent\textbf{Audit and Mark Exclusion:}
No ballot must be both audited and cast $\mathsf{A_{udit}}[i]\cdot \mathsf{M_{ark}}[i]=0$ for all $i < n$.

\noindent\textbf{Tally correctness:}
For each candidate $c\in\{0,\dots,\mathcal{C}-1\}$, the published tally $\mathsf{Sum}_c$ is equal to the sum of $\mathsf{M_{ark}}[i]$ over the
stream $\{c, c+\mathcal{C}, c+2\mathcal{C},\dots\}$, enforced by a strided accumulator (shift by $\omega^\mathcal{C}$) with boundary conditions
for the first/last stream elements.

\paragraph{Batched quotient argument.}
Let $k=17+\mathcal{C}$ be the number of vanishing polynomials. 
Using Fiat-Shamir, derive $\alpha \stackrel{\$}{\leftarrow} \mathbb{F}$ and define the batched vanishing polynomial
\begin{equation*}
P_{\mathsf{vanish}}(X)=\sum_{i=1}^{k}\alpha^{i-1}\,P_i(X).
\end{equation*}

Then form the quotient
\[
Q(X)=\frac{P_{\mathsf{vanish}}(X)}{Z_H(X)} \quad \text{where } Z_H(X)=X^n-1.
\]
If all constraints hold on $\Omega$, $Q(X)$ exists as a polynomial.  

\paragraph{Proof.}
The EA commits to the masked witness and auxiliary polynomials required by the constraints
($\mathsf{A_{udit}},\mathsf{M_{ark}}$ and the block-sum/accumulator polynomials) and to $Q$,
then opens them at a single Fiat-Shamir point $\zeta\in\mathbb{F}$.  

\paragraph{Verification.}
From the opened values at $\zeta$, the verifier reconstructs $P_{\mathsf{vanish}}(\zeta)$ and checks
\begin{equation*}
P_{\mathsf{van}}(\zeta) \stackrel{?}{=} Q(\zeta)\cdot(\zeta^n-1),
\end{equation*}
accepting iff the check passes under $\mathsf{KZG.Verify}$.  

\subsection{Voter Verification Proofs}
Voter verification is a \emph{separate} zero-knowledge proof from the main election proof, but it reuses the same setup and the same committed election polynomials.  

\paragraph{Print audit (spoiled ballots).}
Given a spoiled ballot $\mathcal{B}_j$, the EA opens the commitments for the corresponding index block $\{j\mathcal{C},\dots,j\mathcal{C}+\mathcal{C}-1\}$ to show the ballot was audited and not cast.
There is no need to satisfy the receipt-freeness requirement for audited ballots.

\paragraph{Ballot inclusion (receipt check without revealing the choice).}
To show a voter’s receipt code corresponds to a marked position without revealing which candidate was marked, the EA proves a permutation relation over tuples.
For each $i$, form $(b_i,c_i,m_i)=(\mathsf{B_{ID}}[i],\mathsf{C}_{\mathsf{confirm}}[i],\mathsf{M_{ark}}[i])$ and a shuffled copy
$(b'_i,c'_i,m'_i)=(b_{\sigma(i)},c_{\sigma(i)},m_{\sigma(i)})$ for a secret shuffle $\sigma$.
Using Fiat-Shamir, sample $\alpha,r\stackrel{\$}{\leftarrow} \mathbb{F}$, encode tuples into scalars
$v_i=b_i+\alpha c_i+\alpha^2 m_i$ and $v'_i=b'_i+\alpha c'_i+\alpha^2 m'_i$, define
$V_1[i]=r-v_i$ and $V_2[i]=r-v'_i$, and enforce multiset equality via a grand product accumulator argument.
All resulting checks are expressed as a small set of vanishing polynomials, batched with
a random $\beta$, and verified with a single quotient test exactly as in the main proof.  

After the permutation proof, the EA reveals the $mathcal{C}$ tuples in the shuffled list whose ballot ID equals $\mathcal{B}_j$ via $\mathsf{KZG.Open}$.
Exactly one tuple has $m'=1$, establishing inclusion while the shuffle hides which candidate position was marked.

\paragraph{Receipt correctness (prove a disputed code is \emph{not} on ballot $\mathcal{B}_j$).}
Let the disputed code be $C$. The EA defines a helper indicator polynomial $D(X)$ whose evaluations satisfy
$D(\omega^i)=1$ iff $\mathsf{C}_{\mathsf{confirm}}[i]=C$ using \emph{Fermat's Little Theorem}.
Let $\mathsf{Sel}_j(X)$ be the public selector that is $1$ on indices $\{j\mathcal{C},\dots,j\mathcal{C}+\mathcal{C}-1\}$ and $0$ elsewhere.
The EA proves
\[
z \;=\; \sum_{i=0}^{n-1}\mathsf{Sel}_j(\omega^i)\cdot D(\omega^i) \;=\; 0.
\]
This implies no confirmation code on ballot $\mathcal{B}_j$ is equal to the disputed code $C$ without revealing any of the ballot’s codes.

\section{Security Analysis}

\subsection{Completeness}

\begin{theorem}[Completeness]
    If an honest Prover $\mathcal{P}$ computes the accumulators $Acc_{T_1}(X)$ and $Acc_{T_2}(X)$ according to the backward accumulation rule defined in the protocol, then the Verifier $\mathcal{V}$ accepts with probability 1.
\end{theorem}

\begin{proof}
    The honest prover constructs the backward accumulator such that $Acc_{T_1}(\omega^i) = \prod_{j=i}^{n-1} T_1(\omega^j)$. The protocol enforces constraints via a batched vanishing polynomial $P_{vanish}(X)$.
    \begin{enumerate}
        \item \textbf{Boundary Consistency:} At the last element $X = \omega^{n-1}$, the accumulator is defined as $Acc_{T_1}(\omega^{n-1}) = T_1(\omega^{n-1})$. Consequently, the term $(Acc_{T_1}(X) - T_1(X))$ is zero at this point, satisfying the boundary constraint $P_{vanish1}$.
        \item \textbf{Recursive Consistency:} For all $X \in \Omega$ except $X=\omega^{n-1}$, the recursive definition holds: $Acc_{T_1}(\omega^i) = T_1(\omega^i) \cdot Acc_{T_1}(\omega^{i+1})$. This ensures the constraint $P_{vanish3}$ evaluates to zero on the relevant domain.
        \item \textbf{Product Equality:} Since the tuples are permutations, the total products over $\Omega$ are equal. Thus, $Acc_{T_1}(1) = \prod_{x \in \Omega} T_1(x) = \prod_{x \in \Omega} T_2(x) = Acc_{T_2}(1)$, satisfying the equality constraint $P_{vanish5}$.
    \end{enumerate}
    Since all individual constraint polynomials vanish on $\Omega$, $P_{vanish}(X)$ is divisible by the vanishing polynomial $Z_H(X) = X^n - 1$. Therefore, the quotient check $P_{vanish}(\zeta) - Q(\zeta)Z_H(\zeta) \stackrel{?}{=} 0$ holds for any $\zeta \in \mathbb{F}_q$.
    \qed
\end{proof}

\subsection{Knowledge Soundness}

\begin{theorem}[Knowledge Soundness]
    The protocol satisfies knowledge soundness in the Algebraic Group Model. If a malicious prover ${\mathcal{P}}$ convinces $\mathcal{V}$ with non-negligible probability $\epsilon$, there exists an efficient Extractor $\mathcal{E}$ that outputs polynomials $T(X)$ and $T'(X)$ such that the set of their evaluations on $\Omega$ are permutations of each other.
\end{theorem}

\begin{proof}
    In the AGM, the Extractor $\mathcal{E}$ observes the commitments sent by ${\mathcal{P}}$. Since ${\mathcal{P}}$ outputs valid commitments $[Acc_{T_1}], [Acc_{T_2}]$, it must know the underlying polynomials.
    
    If $\mathcal{V}$ accepts, the equation $P_{vanish}(\zeta) = 0$ holds at a random challenge $\zeta \leftarrow \mathbb{F}_q$. By the Schwartz-Zippel Lemma, this implies that $P_{vanish}(X)$ is divisible by $Z_H(X)$ with overwhelming probability. 
    We unroll these constraints to prove the validity of the statement:

    \begin{enumerate}
        \item \textbf{Unrolling the Accumulator:}
        From the boundary constraint ($P_{vanish1} \equiv 0$), we have $Acc_{T_1}(\omega^{n-1}) = T_1(\omega^{n-1})$.
        From the constraint ($P_{vanish3} \equiv 0$), for any $x \in \Omega$ except $X= \omega^{n-1}$, $Acc_{T_1}(x) = T_1(x) \cdot Acc_{T_1}(\omega x)$.
        With this backwards accumulation, we determine that $Acc_{T_1}(1)$ stores the complete product:
        \begin{equation}
            Acc_{T_1}(1) = \prod_{i=0}^{n-1} T_1(\omega^i)
        \end{equation}
        Similarly, we derive $Acc_{T_2}(1) = \prod_{i=0}^{n-1} T_2(\omega^i)$.

        \item \textbf{Equality of Multisets:}
        The final constraint ($P_{vanish5} \equiv 0$) ensures $Acc_{T_1}(1) = Acc_{T_2}(1)$. Substituting the definitions of $T_1$ and $T_2$:
        \begin{equation}
            \prod_{x \in \Omega} (r - T(x)) = \prod_{x \in \Omega} (r - T'(x))
        \end{equation}
        This equation implies equality between two polynomials in the variable $r$. Since $r$ is chosen uniformly at random by the verifier \emph{after} the commitments to $T(X)$ and $T'(X)$, the equality holds identically with overwhelming probability. 
        Therefore, these polynomials are considered to be \emph{set equal}. Thus, $T'$ is a valid permutation of $T$.
    \end{enumerate}
    \qed
\end{proof}

\subsection{Honest-Verifier Zero-Knowledge}

\begin{theorem}[HVZK]
    The protocol is Honest-Verifier Zero-Knowledge. There exists a Simulator $\mathcal{S}$ that outputs a transcript indistinguishable from a real prover's trace.
\end{theorem}

\begin{proof}
   The Simulator $\mathcal{S}$ operates as follows:

\begin{enumerate}
    \item \textbf{Challenge Sampling:} $\mathcal{S}$ samples random challenges $r, \beta, \zeta \leftarrow \mathbb{F}_q$ exactly as the honest verifier would.
    
    \item \textbf{Simulate Commitments:} $\mathcal{S}$ outputs random group elements for $[Acc_{T_1}], [Acc_{T_2}], [T_1], [T_2]$. Due to the hiding property of KZG (with blinding), these are indistinguishable from real commitments.
    
    \item \textbf{Simulate Evaluations:}
    \begin{itemize}
        \item $\mathcal{S}$ chooses random values for evaluations $\bar{T}_1, \bar{T}_2, \overline{Acc}_{T_1}, \overline{Acc}_{T_2}$ at $\zeta$ and required shifted points (e.g., $\omega\zeta$). This is valid because the blinded polynomials act as One-Time Pads at any point $\zeta \notin \Omega$.
        
        \item $\mathcal{S}$ must ensure the verification equation holds: $P_{vanish}(\zeta) - Q(\zeta)Z_H(\zeta) = 0$.
        
        \item $\mathcal{S}$ computes the value of $P_{vanish}(\zeta)$ using the randomly sampled evaluations and the formulas for $Z_1, Z_2, Z_3$ evaluated at $\zeta$.
        
        \item $\mathcal{S}$ then \textit{sets} the evaluation of the quotient polynomial $\bar{Q} = Q(\zeta)$ specifically to satisfy the equation:
        \[
        \bar{Q} = \frac{P_{vanish}(\zeta)}{Z_H(\zeta)}
        \]
        Since $\zeta$ is random, $Z_H(\zeta) \neq 0$, making this division valid.
    \end{itemize}
    
    \item \textbf{Transcript Consistency:} The tuple of commitments, challenges, and evaluations $(\dots, \bar{Q})$ satisfies the algebraic verification check by construction. Because the evaluations of blinded polynomials are uniformly distributed, the simulated transcript is statistically indistinguishable from a real transcript. 
\end{enumerate}
\end{proof}

\section{Implementation and Performance Evaluation}

We describe a production-ready implementation of Zeeperio that takes the
polynomial relations from (Section 3- section 4) and verifies
them on Ethereum under gas constraints. 
The system has two parts:
\begin{itemize}
  \item an off-chain prover implemented in Rust that constructs the necessary
  witness columns, forms KZG commitments, and produces batched openings.
  \item an on-chain verifier implemented as a Solidity smart contract that
  recomputes Fiat--Shamir challenges, checks KZG openings using BN254 pairings,
  and validates the aggregated vanishing identities at a single challenge point $\zeta$.
\end{itemize}

\input{figures/pipeline.tex}

\subsection{Implementation}

\paragraph{Off-chain prover.}
An election instance is defined by $\mathcal{B}$ ballots and $\mathcal{C}$ candidates, yielding $\mathcal{P}=\mathcal{B}\mathcal{C}$ ballot-candidate
positions. We pad to the next power of two $n\ge P$ and define the evaluation
domain $H=\{\omega^0,\ldots,\omega^{n-1}\}$ where $\omega$ is an $n$th root of
unity. Each length-$n$ column is represented as evaluations on $H$, and the prover deterministically derives the auxiliary columns
required by the protocol.

All constraints are enforced via vanishing identities over $H$. For each
constraint we form a polynomial $V_i(X)$ intended to vanish on~$H$, and we
define the corresponding quotient $Q_i(X)$ such that

\begin{equation*}
  V_i(X) \;=\; Q_i(X)\cdot Z_H(X), 
\end{equation*}
where $Z_H(X)=X^n-1$ is the vanishing polynomial for $H$. 
Instead of proving each constraint separately, the prover aggregates them using a
Fiat-Shamir challenge $\alpha$ and proves a single identity at $\zeta$:

\begin{equation*}
 p_{\textsf{vanish}}(\zeta)
  \;:=\;
  \sum_i \alpha^i V_i(\zeta)
  \;=\;
  Q(\zeta)\cdot Z_H(\zeta),
\end{equation*}
where $Q$ is the aggregated quotient polynomial committed by the prover.

To satisfy the zero-knowledge property, the prover applies \emph{hiding KZG} commitments, where it
adds a blinding term derived from a $\gamma\cdot g$ SRS basis. Additionally, the prover uses 
\emph{$Z$-masking} for witness polynomials not meant to be revealed off-domain, and randomizes them as
$f'(X)=f(X)+\rho(X)\,Z_H(X)$, which preserves evaluations on $H$.

\paragraph{Fiat-Shamir transcript.}
Challenges are derived non-interactively by hashing public inputs and serialized
commitments in a fixed order. The transcript yields $(\alpha,\zeta)$ for the main
proof and additional challenges for the inclusion/shuffle proof.
Both prover and verifier must share \emph{exact} serialization rules
(little-endian field encoding and compressed group encoding), otherwise valid
proofs will be rejected.

\paragraph{Batched openings and ABI export.}
To keep calldata and gas predictable, the prover batches multiple openings at a
common point using a folding scalar $\gamma$ and outputs a single witness group
element per point. The exported ABI payload contains public inputs, labeled
commitments, a list of opening batches (each with point, $\gamma$, labels, opened
values, and blinding scalars), and the transcript scalars.

\paragraph{On-chain verifier.}
The verifier exposes three entrypoints, \texttt{verifyMain(bytes)}, \texttt{verifyInclusion(bytes)}, and \texttt{verifyReceipt(bytes)}.
Each entrypoint decodes calldata into a structured proof, recomputes transcript
challenges from the decoded statement and commitments, and rejects if challenges
do not match.

For each opening batch at point $x$, the contract folds the relevant commitments
and values, then checks a single KZG pairing equation via the BN254 pairing
precompile. After all the openings have been validated, the contract reconstructs the required
evaluations, computes the proof $p_{\textsf{vanish}}(\zeta)$, and checks
\begin{equation*}
  p_{\textsf{vanish}}(\zeta)=Q(\zeta)\,(\zeta^n-1).
\end{equation*}

To keep the EVM logic minimal, commitments and opened values are tagged by
16-bit labels which help the verifier locate required evaluations via simple scans over
decoded arrays.

\subsection{Performance Evaluation}

We evaluate Zeeperio along the three axes:
(i) prover time, (ii) verifier time (including decoding), and (iii) calldata size.
We report metrics separately for the main proof and the two voter verification proofs.


\subsubsection{Benchmark configuration}

As shown in Table \ref{tab:election}, we report metrics for a single election instance with
$B=100,000$ ballots and $C=8$ candidates. This yields $P=BC=800{,}000$
ballot-candidate positions, which we pad to the next power-of-two
$n=\textsf{pow2}(P)=2^{20}=1{,}048{,}576$ to define the evaluation domain
$H=\{\omega^0,\ldots,\omega^{n-1}\}$.
For this election, we allocate $10\%$ of ballots to print audits.
\input{figures/election.tex}


\subsubsection{Metrics reported}

We report three deployability metrics for each proof kind:
(i) prover time, (ii) proof/calldata size, and (iii) on-chain gas.


\paragraph{Proof size.}
We report: number of commitments, number of opening points, total opened labels,
and ABI calldata length in bytes.

\paragraph{On-chain cost.}
We report gas used by \texttt{verifyMain}, \texttt{verifyInclusion}, and
\texttt{verifyReceipt}.

\input{figures/evaluations.tex}