% !TEX root = ../main.tex

We now turn to Zeeprio and begin with coercion resistance. The key observation we call non-expansivity: Zeeprio does not reveal any information beyond what is already revealed by Eperio. More precisely, any information available to a coercer from a Zeeprio transcript can be derived from an Eperio transcript, possibly with weaker assurance. Consequently, Zeeprio cannot be less coercion resistant than Eperio: any ballot secrecy property that holds for Eperio continues to hold when augmented with Zeeprio’s additional verification artifacts. 

In particular, if non-expansivity holds, Zeeprio inherits at least the level of ballot secrecy established for Eperio by Basin \etal~\cite{BDGR21}, namely receipt-freeness under their table-based definition. Moreover, Zeeprio may also inherit coercion resistance in the stronger sense of Küsters \etal~\cite{KTV10c}, provided one accepts the conjecture that replacing Scantegrity II’s switchboard with Eperio does not reduce ballot secrecy in any meaningful way.

We formalize this in the following lemma:

\begin{lemma}[Non-Expansive Ballot Secrecy under Transcript Augmentation]
Let $\Pi$ be a protocol and let $\Pi^{+}$ be an augmentation that, on the same underlying execution, produces a coercer view
$T^{+} := (T,Z)$, where $T$ is the coercer view in $\Pi$ and $Z$ is an additional transcript component.
Assume that for every probabilistic polynomial-time distinguisher $\mathcal{D}$ and every security parameter $\lambda$,
there exists a probabilistic polynomial-time algorithm $\mathsf{Sim}$ such that
\[
\Bigl|\Pr[\mathcal{D}(T,Z)=1] - \Pr[\mathcal{D}(T,\mathsf{Sim}(T))=1]\Bigr|
\]
is negligible as a function of $\lambda$.
\end{lemma}

Under this lemma, $\Pi^{+}$ is not less private than $\Pi$ for any ballot secrecy notion whose experiment depends on the protocol only through
the coercer view. In particular, for any such ballot secrecy experiment and any probabilistic polynomial-time adversary
$\mathcal{A}$ interacting with $\Pi^{+}$, there exists a probabilistic polynomial-time adversary
$\mathcal{B}$ interacting with $\Pi$ such that the difference between the success probabilities of
$\mathcal{A}$ and $\mathcal{B}$ in their respective experiments is negligible in $\lambda$.

 In the special case where $Z$ is efficiently computable from $T$ (and public parameters), the simulator
$\mathsf{Sim}$ may be chosen to simply compute $Z$ from $T$. In other words, $\mathsf{Sim}$ is pure post-processing. This will be the dominant case for Zeeperio.

To reason about the non-expansive ballot secrecy of Zeeprio, we separate two concerns: (i) the \emph{cryptographic} claim that the proof a polynomial vanishes is zero-knowledge and proves nothing beyond the statement that the polynomial vanishes; and (i) the \emph{semantic} claim that the constraints implied by Zeeperio are non-expansive over an Eperio transcript.

Starting with the \emph{cryptographic} claim, we directly assume the PIOP used by Zeeprio satisfies the standard zero-knowledge property: its proof transcript reveals no information beyond the fact that the asserted algebraic relations are true. Concretely, as formalized for PLONK-style polynomial IOPs, there exists a simulator that, given only the statement that the constraints are satisfied, produces a transcript that is indistinguishable from an honestly generated one. This simulator construction is explicit in the PIOP literature~\cite{Sef24,Lip25} and does not depend on the particular semantics of the underlying constraints, so we do not reprove anything regarding this.

We do however add two important implementation details that allow the simulation to go through. The first is that the polynomial commitment scheme needs to be hiding. When using KZG commitments~\cite{KZG10}, it is sufficient to use their second construction informally referred to as the Pedersen-variant of KZG. The second is that the PIOP proof will open committed polynomials at random challenge points. If the adversary has a guess as to the specific polynomial under commitment, it can use this random challenge to confirm its guess. To prevent this, polynomials should incorporate extra random points (off-domain) at interpolation time, where the number of points exceed the number of points that will be eventually opened on the given polynomial. This lacks a standard name in the literature and we propose calling it the MBKM heuristic~\cite{MBKM19} after it was popularized in the zk-SNARK system Sonic.

We spend the rest of the proof dealing with the \emph{semantic} claim: the algebraic relations asserted by Zeeprio’s constraint system encode no more information than what is already revealed by Eperio’s verification logic.

Following the original paper~\cite{ECHA10} and the Basin \etal paper~\cite{BDGR21}, we model Eperio's data structure as an election table for $B$ ballots (ranging over  $b \in \{1,\dots,B\}$) and $C$ candidates ranging over $j \in \{1,\dots,C\}$. The table has the following columns:

Following the original Eperio paper~\cite{ECHA10} and the formulation of Basin \etal~\cite{BDGR21}, we model Eperio’s data structure as a canoncical election table with a single row index $r \in \{1,\dots,B\cdot C\}$ where each row corresponds to a unique ballot–position pair. Intuitively, rows are ordered first by ballot and then by candidate position: for ballot $b$, its $C$ candidate slots occupy $C$ consecutive rows, and advancing the row index past these $C$ positions corresponds to moving to the next ballot. We write the table as having the following columns:

\begin{itemize}
\item $\mathsf{U}[r]$ contains a unique identifier for the $j$th candidate slot on ballot $b$.

\item $\mathsf{C}[r]$ contains a confirmation code associated with position $r$, used for receipt checking when that position is revealed.

\item $\mathsf{M}[r] \in \{-1,0,1\}$ contains the mark value, equal to $1$ if and only if ballot $b$ marks position $j$, $-1$ if it is part of a print audit, and $0$ if unmarked or unused.

\item $\mathsf{S}[r]$ contains the candidate name printed on position $r$.

\end{itemize}

Both the original paper~\cite{ECHA10} and the Basin \etal paper~\cite{BDGR21} model Eperio with a ballot where the order of the candidates in random on each ballot (so knowing a voter voted for the second candidate in the list does not reveal which candidate was voted for). Such a ballot is associated with the Pret a Voter system and are called Pret a Voter ballots~\cite{RBH+09}. For Eperio to work with confirmation codes instead (ballots based on Scantegrity and Scantegrity II), a code column can be added as above. 

Eperio works out-of-the-box with Scantegrity ballots but does not work with Scantegrity II ballots. The reason is not in the semantics of the table, it is because Eperio commits to data at the granularity of an entire column. Scantegrity II is the same as Scantegrity I with two differences: (1) only the marked codes are revealed and the unmarked codes are secret, and (2) as a consequence, the codes need to be harder to guess and thus longer than Scantegrity. Columnwise commitments are central to Eperio's efficiency and verifiability claims, and are the key cryptographic distinguisher from Scantegrity's Switchboard which it is replacing. In Zeeperio, polynomial commitments provide the best of both worlds: a single commitment can bind an entire column of data, and at reveal time, selective elements can be opened while leaving others hidden. 

The Eperio election table is never revealed in its entirety or all notions of ballot secrecy would be defeated. Instead $\ell$ copies of the table are permuted randomly by row and committed to before the election (with a blank $\widetilde{\mathsf{M}}[r]$ column). After the election, the election authority fills in $\widetilde{\mathsf{M}}[r]$ for each permuted table and commits to it. After committing, a cut-and-choose mechanism reveals either $(\widetilde{\mathsf{U}}[r], \widetilde{\mathsf{C}}[r],\widetilde{\mathsf{M}}[r])$ or it reveals $(\widetilde{\mathsf{M}}[r], \widetilde{\mathsf{S}}[r])$. The former is used by voters to check their receipt. The latter is used to compute the final tally. Every table should be consistent with the same receipt information and election result, and analysis shows that inconsistencies will be caught with probability $2^{-\ell}$. Since the protocol never reveals both the unique identifier or confirmation code and the selected candidate for the same table, it preserve a secret ballot. 

Eperio supports different ballot styles. For Pret a Voter ballots, there is no $\widetilde{\mathsf{C}}[r]$ column and the protocol works the same otherwise. For Scantegrity ballots, $\widetilde{\mathsf{C}}[r]$ is revealed in its entirety as specified above. For Scantegrity II ballots, only marked codes are revealed: $\widetilde{\mathsf{C}}[r]\leftarrow\widetilde{\mathsf{C}}[r]\circ\widetilde{\mathsf{M}}[r]$. Zeeperio provides the same support but since the main body of the paper describes Scantegrity II ballots, we will align Zeeperio's constraints with a description of Eperio for Scantegrity II ballots. 

Eperio handles print audit ballots differently (but equivalently as we will prove below) from Zeeperio. Eperio introduces an auxiliary \emph{linkage list}. For each print audit position $r$, the EA specifies the row index $\rho$ such that $\widetilde{\mathsf{U}}[\rho]$ corresponds to that audited position in every table copy. It does this after updating the mark column and before the cut-and-choose. This effectively allows the entire ballot to be opened up for just these specified ballots, which enables the auditor to check that the confirmation codes are printed beside the correct candidate names (where correct means consistent with the Eperio table). 

We are now ready to walk through each Zeeperio constraint and argue the constraint is non-expansive over what Eperio provides.  

\vanishP{V_{c1.1}(X)\ &:=\ \mathsf{Audit}(X)\,\mathsf{Z}_{\mathsf{head}}(X)}

This constraint enforces that the audit indicator is zero on all padding rows. Unlike other constraints, this statement is not an Eperio verification condition: Eperio has no padding rows and therefore makes no claim about them. Instead, this constraint is an artifact of embedding the Eperio table into a fixed-size polynomial domain. From a privacy perspective, the constraint is a benign transcript augmentation. 

To deterministically construct a Zeeprio witness from an Eperio execution, the simulator first derives the Zeeprio indicator columns from the Eperio mark column by defining $\mathsf{Audit}(r):=\mathbf{1}[M(r)=-1]$ and $\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$. The simulator then embeds these values into a fixed evaluation domain of size $N$ by placing the $B\cdot C$ real ballot-position rows into the non-padding region of the domain and appending $N-(B\cdot C)$ padding rows on which it sets $\mathsf{Audit}=0$ (and likewise $\mathsf{Mark}=0$). This construction depends only on the public parameters $N$, $B$, and $C$, and not on any voting data; consequently, the padding rows are fully simulatable and the constraint cannot expand the information available to a coercer.

\vanishP{V_{c1.2}(X)\ &:=\ \mathsf{Audit}(X)\bigl(\mathsf{Audit}(X)-1\bigr) }

This constraint enforces that the audit indicator is boolean. Given the construction above, this is immediate: the simulator defines $\mathsf{Audit}(r):=\mathbf{1}[M(r)=-1]$ on real ballot-position rows and sets $\mathsf{Audit}(r)=0$ on padding rows. Since the Eperio mark column $M(r)$ takes values in $\{-1,0,1\}$, the indicator map ensures $\mathsf{Audit}(r)\in\{0,1\}$ for all rows, and therefore $\mathsf{Audit}(r)\bigl(\mathsf{Audit}(r)-1\bigr)=0$ holds identically. As with the previous constraint, this property is enforced by the deterministic embedding and padding procedure and does not correspond to any additional Eperio verification condition. Consequently, it constitutes a benign transcript augmentation and does not expand the information available to a coercer.

\vanishP{V_{c1.3}(X)\ &:=\ \bigl(\mathsf{Sel}_{\mathsf{blk}}(X)\mathsf{BlkSum}_{\mathsf{Audit}}(X)\bigr)\bigl(\mathsf{Sel}_{\mathsf{blk}}(X)\mathsf{BlkSum}_{\mathsf{Audit}}(X)-\mathcal{C}\bigr)}

This constraint enforces whole-ballot audit consistency: for each ballot block, either none of its positions are designated for audit or all $\mathcal{C}$ positions are. 

In Eperio, audit status is encoded in the mark column by a distinguished value ($\widetilde{\mathsf{M}}=-1$) and the cut-and-choose opens, for each permuted
table copy, either the receipt-facing view $(\widetilde{\mathsf{U}},\widetilde{\mathsf{C}},\widetilde{\mathsf{M}})$ or the tally-facing view $(\widetilde{\mathsf{M}},\widetilde{\mathsf{S}})$. From any copy in which $(\widetilde{\mathsf{U}},\widetilde{\mathsf{C}},\widetilde{\mathsf{M}})$ is opened, the simulator reads the values
$\widetilde{\mathsf{U}}$ and $\widetilde{\mathsf{M}}$ and deterministically reconstructs the audit indicator $\mathsf{Audit}(r):=\mathbf{1}[M(r)=-1]$ indexed by the underlying row identifiers. Using $\mathsf{U}$, the simulator then places these rows into a fixed canonical order in which the $\mathcal{C}$ positions of each ballot occupy a contiguous block.

Because the Eperio transcript fixes print audits at the ballot level, the reconstructed audit indicator has the property that, within each such block, either all $\mathcal{C}$ rows have $\mathsf{Audit}=1$ or none do. The simulator therefore computes, for each block, a block sum that is always either $0$ or $\mathcal{C}$, and the polynomial
$\mathsf{Sel}_{\mathsf{blk}}(X)\mathsf{BlkSum}_{\mathsf{Audit}}(X)$ takes only these two values. Consequently, the constraint polynomial vanishes identically. This reasoning relies only on information already present in the Eperio transcript and the simulator’s deterministic reindexing, and does not introduce any additional information beyond the Eperio view.

\vanishP{V_{c1.4}(X)\ &:=\ \bigl(\mathsf{Acc}_{\mathsf{Audit}}(X)-\mathsf{Audit}(X)+\mathsf{Acc}_{\mathsf{Audit}}(\omega X)\bigr)\cdot(X-\omega^{n-1})}

This constraint enforces contiguity of audit blocks: within the canonical row ordering used by Zeeprio, the audit indicator is constant across consecutive rows belonging to the same ballot block. Informally, it states that $\mathsf{Audit}(r)$ can change value only at block boundaries and nowhere else.

Starting from an Eperio execution, the simulator reconstructs the audit indicator $\mathsf{Audit}(r):=\mathbf{1}[M(r)=-1]$ as before and then reindexes rows using the identifier column $\mathsf{U}$ so that the $\mathcal{C}$ positions of each ballot occupy $\mathcal{C}$ consecutive rows. By construction of this canonical
ordering, $\mathsf{Audit}(r)$ is constant on each block and may change only between the last row of one block and the first row of the next. The accumulator polynomial $\mathsf{Acc}_{\mathsf{Audit}}$ is then defined by the simulator so that it increments exactly when $\mathsf{Audit}$ transitions between blocks. The factor $(X-\omega^{n-1})$ excludes the wraparound case at the end of the domain, ensuring the relation is enforced only for valid adjacent rows.

Because this accumulator is computed deterministically from the reconstructed $\mathsf{Audit}$ column and the fixed block layout, the relation holds identically in the simulator’s construction. As in the previous constraints, it follows directly from the Eperio semantics together with the simulator’s reindexing and does not reveal any additional information beyond what is already present in the Eperio transcript.

\vanishP{V_{c1.5}(X)\ &:=\ \bigl(\mathsf{Acc}_{\mathsf{Audit}}(X)-\mathsf{Audit}(X)\bigr)\cdot \mathsf{Mask}_{n-1}(X)}

This constraint pins the accumulator to the audit indicator at the start of the domain: it enforces that
$\mathsf{Acc}_{\mathsf{Audit}}$ is initialized consistently with $\mathsf{Audit}$ on the first row (and only the first row,
as selected by $\mathsf{Mask}_{n-1}$). Given the simulator’s construction from the Eperio transcript, this is immediate.
After reconstructing the canonical audit indicator $\mathsf{Audit}(r)$ (from the opened $(\widetilde{\mathsf{U}},\widetilde{\mathsf{M}})$
data) and fixing the canonical row order, the simulator defines the accumulator column $\mathsf{Acc}_{\mathsf{Audit}}$
so that it satisfies the intended recurrence across adjacent rows; it then sets the initial value
$\mathsf{Acc}_{\mathsf{Audit}}$ on the masked start row to equal $\mathsf{Audit}$ on that row. With this explicit
initialization, the masked product is identically zero and the constraint holds by construction. As with the previous
accumulator constraints, this is an embedding/consistency check internal to Zeeprio’s witness representation and does not
assert any new election-specific fact beyond what the Eperio transcript already fixes.

\vanishP{V_{c1.6}(X)\ &:=\ \bigl(\mathsf{Acc}_{\mathsf{Audit}}(X)-\mathsf{Sum}_{\mathsf{Audit}\times\mathcal{C}}\bigr)\cdot \mathsf{Mask}_{0}(X)}

This constraint fixes the accumulator’s final value: it enforces that on the last row of the domain (selected by
$\mathsf{Mask}_{0}$), the audit accumulator equals the total number of audited positions, expressed as the precomputed
sum $\mathsf{Sum}_{\mathsf{Audit}\times\mathcal{C}}$. In the simulator’s construction, once $\mathsf{Audit}(r)$ has been
reconstructed from the Eperio transcript and placed into canonical ballot blocks of size $\mathcal{C}$, the simulator can
compute the total number of audited positions deterministically as $\sum_r \mathsf{Audit}(r)$; by whole-ballot audit
consistency (c1.3), this is equal to $\mathcal{C}$ times the number of audited ballots. The simulator then sets the
public value $\mathsf{Sum}_{\mathsf{Audit}\times\mathcal{C}}$ to this same quantity and defines
$\mathsf{Acc}_{\mathsf{Audit}}$ so that its last entry equals the computed total. With these choices, the masked
difference is zero and the constraint holds by construction, relying only on information already present in the Eperio
transcript.

\vanishP{V_{c2.1}(X)\ &:=\ \mathsf{Mark}(X)\,\mathsf{Z}_{\mathsf{head}}(X)}

This constraint enforces that the mark indicator is zero on all padding rows. As in constraint c1.1, Eperio has no notion of
padding rows; they are introduced only to embed the Eperio table into a fixed-size polynomial domain. In the simulator’s
construction, the mark indicator is derived from the Eperio mark column as
$\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$ on real ballot-position rows and is set to $0$ on padding rows. Consequently,
$\mathsf{Mark}(X)\,\mathsf{Z}_{\mathsf{head}}(X)$ vanishes identically. This constraint is therefore handled in exactly the
same way as c1.1: it is a benign transcript augmentation enforced by deterministic padding and does not expand the
information available to a coercer.

\vanishP{V_{c2.2}(X)\ &:=\ \mathsf{Mark}(X)\bigl(\mathsf{Mark}(X)-1\bigr)}

This constraint enforces that the mark indicator is boolean. Given the simulator’s construction, this is immediate.
In Eperio, the mark column $M(r)$ takes values in $\{-1,0,1\}$, where $1$ denotes a marked position. The simulator defines
$\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$ on real ballot-position rows and sets $\mathsf{Mark}(r)=0$ on padding rows. Hence
$\mathsf{Mark}(r)\in\{0,1\}$ for all rows, and $\mathsf{Mark}(r)\bigl(\mathsf{Mark}(r)-1\bigr)=0$ holds identically.
As with c1.2, this property follows directly from the deterministic embedding and padding procedure and constitutes a
benign transcript augmentation that does not expand the information available to a coercer.

\vanishP{V_{c2.3}(X)\ &:=\ \bigl(\mathsf{Sel}_{\mathsf{blk}}(X)\mathsf{BlkSum}_{\mathsf{Mark}}(X)\bigr)\bigl(\mathsf{Sel}_{\mathsf{blk}}(X)\mathsf{BlkSum}_{\mathsf{Mark}}(X)-1\bigr)}

This constraint enforces \emph{single-mark per ballot}: within each ballot block, the total number of marked positions is
either $0$ or $1$. In Eperio, each ballot may record at most one vote, and this fact is reflected in the mark column
$M(r)\in\{-1,0,1\}$, where at most one position per ballot has value $1$. From the Eperio transcript, the simulator
reconstructs the canonical mark indicator $\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$ and reindexes rows so that each ballot
occupies a contiguous block of $\mathcal{C}$ rows. Under this canonical ordering, the block sum
$\mathsf{BlkSum}_{\mathsf{Mark}}$ is therefore always either $0$ or $1$ on each block, and the constraint polynomial
vanishes identically. As with the previous block-level constraints, this follows directly from the Eperio semantics and
the simulator’s deterministic reindexing, and does not introduce any additional information beyond the Eperio view.

\vanishP{V_{c2.4}(X)\ &:=\ \bigl(\mathsf{Acc}_{\mathsf{Mark}}(X)-\mathsf{Mark}(X)+\mathsf{Acc}_{\mathsf{Mark}}(\omega X)\bigr)\cdot(X-\omega^{n-1})}

This constraint enforces contiguity of marked positions within each ballot block: in the canonical row ordering,
$\mathsf{Mark}(r)$ may change only at block boundaries and not within a block. From the Eperio transcript, the simulator
reconstructs the canonical mark indicator $\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$ and reindexes rows using $\mathsf{U}$ so
that the $\mathcal{C}$ positions of each ballot form a contiguous block. Because Eperio allows at most one marked
position per ballot, $\mathsf{Mark}(r)$ is constant on each block except possibly for a single transition. The simulator
defines the accumulator $\mathsf{Acc}_{\mathsf{Mark}}$ to track these transitions across adjacent rows, and the factor
$(X-\omega^{n-1})$ excludes the wraparound case at the end of the domain. With this deterministic construction, the
relation holds identically. As in the corresponding audit constraint c1.4, this accumulator condition follows directly
from the Eperio semantics together with the simulator’s reindexing and does not reveal any additional information beyond
the Eperio transcript.

\vanishP{V_{c2.5}(X)\ &:=\ \bigl(\mathsf{Acc}_{\mathsf{Mark}}(X)-\mathsf{Mark}(X)\bigr)\cdot \mathsf{Mask}_{n-1}(X)}

This constraint fixes the initialization of the mark accumulator: it enforces that on the first row of the domain
(selected by $\mathsf{Mask}_{n-1}$), the accumulator $\mathsf{Acc}_{\mathsf{Mark}}$ equals the mark indicator
$\mathsf{Mark}$. In the simulator’s construction, once $\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$ has been reconstructed from
the Eperio transcript and rows have been placed into the canonical block ordering, the simulator defines the accumulator
$\mathsf{Acc}_{\mathsf{Mark}}$ to satisfy the intended recurrence across adjacent rows and explicitly sets its initial
value to match $\mathsf{Mark}$ on the first row. With this deterministic initialization, the masked difference is zero and
the constraint holds identically. As with the corresponding audit constraint c1.5, this is an internal consistency
condition of the accumulator and does not introduce any additional information beyond what is already present in the
Eperio transcript.

\vanishP{V_{c2.6}(X)\ &:=\ \bigl(\mathsf{Acc}_{\mathsf{Mark}}(X)-\mathsf{Sum}_{\mathsf{Mark}}\bigr)\cdot \mathsf{Mask}_{0}(X)}

This constraint fixes the final value of the mark accumulator: it enforces that on the last row of the domain (selected by
$\mathsf{Mask}_{0}$), the accumulator $\mathsf{Acc}_{\mathsf{Mark}}$ equals the total number of marked positions,
denoted $\mathsf{Sum}_{\mathsf{Mark}}$. In the simulator’s construction, once the canonical mark indicator
$\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$ has been reconstructed and rows have been placed into contiguous ballot blocks,
the simulator computes $\mathsf{Sum}_{\mathsf{Mark}}=\sum_r \mathsf{Mark}(r)$ deterministically from the Eperio transcript.
Because Eperio allows at most one marked position per ballot, this sum equals the total number of cast ballots. The
simulator then defines $\mathsf{Acc}_{\mathsf{Mark}}$ so that its final entry equals this value, and the masked difference
vanishes identically. As with the preceding accumulator constraints, this is a bookkeeping condition enforced by the
simulator’s construction and does not expand the information available to a coercer.

\vanishP{V_{c3.1}(X)\ :=\ \mathsf{Audit}(X)\,\mathsf{Mark}(X)}

This constraint enforces mutual exclusion between auditing and voting: no ballot position may be both marked as a vote and
designated for audit. In the Eperio model, this property is built into the semantics of the mark column $M(r)$, which takes
values in $\{-1,0,1\}$, where $-1$ denotes a print-audited position and $1$ denotes a marked (voted) position. These cases
are disjoint by definition. Under the simulator’s construction, $\mathsf{Audit}(r):=\mathbf{1}[M(r)=-1]$ and
$\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$, so for every row at most one of these indicators can be $1$. Consequently,
$\mathsf{Audit}(r)\,\mathsf{Mark}(r)=0$ holds identically on all real ballot-position rows, and also on padding rows where
both indicators are set to $0$. As with the previous constraints, this condition follows directly from the Eperio mark
semantics and the simulator’s deterministic embedding, and does not introduce any additional information beyond what is
already present in the Eperio transcript.

\vanishP{V_{c4.1}(X)\ &:=\ \bigl(\mathsf{Acc}_{\mathsf{Vote}}(X)-\mathsf{Mark}(X)+\mathsf{Acc}_{\mathsf{Vote}}(\omega^{\mathcal{C}}X)\bigr)\cdot \mathsf{Mask}_{\mathsf{tail}}(X) }

This constraint enforces per-ballot vote accumulation: it ensures that the vote accumulator
$\mathsf{Acc}_{\mathsf{Vote}}$ advances by exactly the mark value once per ballot block, rather than once per row. In the
canonical ordering constructed by the simulator, the $\mathcal{C}$ rows corresponding to a single ballot form a
contiguous block, and $\omega^{\mathcal{C}}X$ points to the next block. Starting from the Eperio transcript, the simulator
reconstructs the canonical mark indicator $\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$ and places rows into these ballot-sized
blocks. It then defines the vote accumulator $\mathsf{Acc}_{\mathsf{Vote}}$ so that it carries forward the accumulated
count from one ballot block to the next and increments by $1$ exactly when a ballot contains a marked position. The mask
$\mathsf{Mask}_{\mathsf{tail}}$ restricts the relation to block boundaries, ensuring that accumulation occurs only once
per ballot. With this deterministic construction, the relation holds identically. As in the previous accumulator
constraints, this condition reflects standard Eperio tally semantics under the simulator’s canonical reindexing and does
not reveal any additional information beyond what is already present in the Eperio transcript.

\vanishP{V_{c4.2}(X)\ &:=\ \bigl(\mathsf{Acc}_{\mathsf{Vote}}(X)-\mathsf{Mark}(X)\bigr)\cdot \frac{\mathsf{Z}_H(X)}{\mathsf{Mask}_{\mathsf{tail}}(X)}}

This constraint enforces that within each ballot block, the vote accumulator mirrors the mark indicator on all non-tail
rows. In the simulator’s canonical ordering, each ballot occupies a contiguous block of $\mathcal{C}$ rows, and exactly
one row in each block (the tail) is designated by $\mathsf{Mask}_{\mathsf{tail}}$. On all other rows of the block, the
accumulator $\mathsf{Acc}_{\mathsf{Vote}}$ is intended to reflect whether a mark has occurred within that ballot. Starting
from the Eperio transcript, the simulator reconstructs the canonical mark indicator
$\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$ and defines $\mathsf{Acc}_{\mathsf{Vote}}$ consistently with this convention across
each block. The factor $\mathsf{Z}_H(X)/\mathsf{Mask}_{\mathsf{tail}}(X)$ restricts the constraint to non-tail rows, so the
relation is enforced exactly where required. With this deterministic construction, the constraint holds identically and,
as with the other vote-accumulator constraints, does not introduce any additional information beyond what is already
present in the Eperio transcript.

\vanishP{V_{c4.3,j}(X)\ &:=\ \bigl(\mathsf{Acc}_{\mathsf{Vote}}(X)-\mathsf{Tally}[j]\bigr)\cdot \frac{\mathsf{Z}_H(X)}{X-\omega^{j}}}

This constraint enforces correctness of the published tally for candidate $j$. It states that, at the designated row
corresponding to candidate $j$, the vote accumulator equals the publicly reported tally value $\mathsf{Tally}[j]$.

Starting from the Eperio transcript, the simulator reconstructs the canonical mark indicator
$\mathsf{Mark}(r):=\mathbf{1}[M(r)=1]$ and places rows into contiguous ballot blocks of size $\mathcal{C}$ using the
identifier column $\mathsf{U}$. As described above, the simulator then defines the vote accumulator
$\mathsf{Acc}_{\mathsf{Vote}}$ so that it increments by one for each ballot whose marked position corresponds to candidate
$j$. Independently, Eperio publishes the final election result, which fixes the tally values $\mathsf{Tally}[j]$.

The factor $\mathsf{Z}_H(X)/(X-\omega^{j})$ restricts the equality to the unique row associated with candidate $j$.
Because the simulator computes $\mathsf{Acc}_{\mathsf{Vote}}$ directly from the Eperio mark data and the canonical
candidate ordering, its value at that row is exactly the number of ballots marked for candidate $j$, which matches the
published tally. Hence the constraint polynomial vanishes identically. As with the previous tally constraints, this
condition relies only on information already present in the Eperio transcript and the simulator’s deterministic
construction, and does not expand the information available to a coercer.

\vanishP{V_{\mathsf{dispute}}(X)\ :=\ \bigl((\mathsf{Code}(X)-c)\cdot \mathsf{Inv}_b(X)-1\bigr)\cdot \mathsf{Mask}^{(b)}_{\mathsf{ballot}}(X)}

This constraint enforces correctness of a voter dispute for ballot $b$: given a confirmation code $c$ presented by the
voter, it checks that $c$ equals the code recorded at the unique marked position on ballot $b$. Note that this
\emph{minimal-disclosure} dispute check is not supported by Eperio in its original Pr\^{e}t-\`a-Voter instantiation,
since that setting has no code column at all. However, Eperio can be instantiated with Scantegrity-style ballots, in
which case it does reveal confirmation-code information via the receipt-facing openings. In the Scantegrity~I variant,
Eperio effectively over-provides: whenever a permuted copy is opened on the receipt-facing side, the transcript exposes
the entire $(\widetilde{\mathsf{U}},\widetilde{\mathsf{C}},\widetilde{\mathsf{M}})$ view for that copy, and thus reveals
many codes beyond the single code a disputing voter needs. By contrast, the dispute constraint above captures exactly the
least information necessary for dispute resolution: it only enforces equality of $\mathsf{Code}(X)$ with the claimed code
$c$ at the marked position of ballot $b$, and is vacuous everywhere else.

Concretely, $\mathsf{Mask}^{(b)}_{\mathsf{ballot}}$ restricts the check to the $\mathcal{C}$ rows corresponding to ballot
$b$, and $\mathsf{Inv}_b$ is chosen so that it is nonzero exactly at the marked row of ballot $b$, thereby isolating that
single table entry. On that row, the constraint reduces to $\mathsf{Code}(X)=c$; on all other rows it imposes no
condition. Thus, in a Scantegrity~I-style Eperio transcript where the code column is available on the receipt-facing
openings, a simulator can reconstruct the relevant $\mathsf{Code}$ value and satisfy the constraint directly. In the
Scantegrity~II-style view (where unmarked codes are masked), the constraint still expresses precisely what is checkable:
it refers only to the marked code that the voter actually learns. In either case, the constraint formalizes dispute
resolution as a minimal disclosure statement, extracting from the Eperio-style code revelations only the single code value
needed to validate the voter’s claim.

\begin{theorem}[Non-expansive ballot secrecy of Zeeprio relative to Eperio]
Let $\Pi$ denote an Eperio election protocol (for the ballot style under consideration) and let $\Pi^{+}$ denote the
augmented protocol that runs the same Eperio execution and additionally publishes a Zeeprio transcript component $Z$
consisting of (i) the Zeeprio commitments and openings corresponding to the embedded election table, and (ii) a
zero-knowledge PIOP/SNARK transcript attesting that the Zeeprio constraints hold for that embedded table.

Then $\Pi^{+}$ is a transcript augmentation of $\Pi$ that is non-expansive for ballot secrecy: for every probabilistic
polynomial-time distinguisher $\mathcal{D}$ and security parameter $\lambda$, there exists a probabilistic
polynomial-time simulator $\mathsf{Sim}$ such that, if $T$ is the coercer view of $\Pi$ and $T^{+}=(T,Z)$ is the coercer
view of $\Pi^{+}$, the quantity
\[
\Bigl|\Pr[\mathcal{D}(T,Z)=1] - \Pr[\mathcal{D}(T,\mathsf{Sim}(T))=1]\Bigr|
\]
is negligible in $\lambda$.
\end{theorem}

\begin{proof}
Fix any Eperio execution and let $T$ denote the resulting coercer view. We define a simulator $\mathsf{Sim}(T)$ that
produces a Zeeprio transcript component $Z$ distributed indistinguishably from a real Zeeprio augmentation of that same
execution.

First, using only the information already present in $T$ (in particular, the published Eperio verification data, opened
views from cut-and-choose, and any public election parameters), the simulator deterministically constructs the Zeeprio
witness representation: it reconstructs the relevant table columns (e.g., the mark and audit indicators derived from the
Eperio mark column), reindexes rows into the canonical ballot-block ordering using the identifier information, and pads
to the fixed evaluation domain. Just above we proved, constraint by constraint, that this
constructed witness satisfies each Zeeprio vanishing relation (including the dispute constraint when applicable to the
ballot style). Therefore, the simulator obtains a valid Zeeprio statement---namely, that there exists a witness for
which all constraint polynomials vanish on the evaluation domain.

Second, the simulator produces the remaining cryptographic artifacts in $Z$ by simulation: it outputs commitments and
openings consistent with the constructed witness, and it invokes the zero-knowledge simulator of the underlying
PIOP/SNARK to generate a proof transcript accepting for the corresponding public statement. By the hiding and
zero-knowledge properties of these primitives, the resulting $Z$ is computationally indistinguishable from the transcript
generated by an honest Zeeprio prover on the same underlying Eperio execution.

Thus for every PPT distinguisher $\mathcal{D}$, the views $(T,Z)$ and $(T,\mathsf{Sim}(T))$ are indistinguishable up to
negligible error, establishing the non-expansive transcript augmentation property claimed. \qed
\end{proof} 



% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
\clearpage
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 













