% !TEX root = ../main.tex

% ====

\section{Security Proof}

\subsection{Overview}

Zeeperio is a component of a voting system, not a full-fledged voting system. We will keep our proof very narrow to the changes Zeeperio introduces because security arguments for most of the other components already exist. Eperio is a `back-end' tabulator that proves the correctness of the election, while leaking no information about how any voter voted from all its transcripts. The `front-end' of the system consists of the paper ballots, how they encode votes, and how voters interact with their voted ballots, audited ballots, and the transcript of the election. The front-end also needs to be receipt-free. Eperio, and by extension Zeeperio, is compatible with multiple front-ends, but we use the example of Scantegrity II.

Scantegrity II is an end-to-end verifiable voting system with paper ballots that are optically scanned. A ballot contains a unique serial number and it contains a unique (per ballot) confirmation code printed beside each candidate in invisible ink. When the voter marks a candidate on the ballot, the voter is able to also read the code. The ballot serial number and the revealed code constitutes the voter's receipt, which they can copy to a piece of paper and bring home. The scanned ballots are provided to a backend system called `the switchboard.' The switchboard prepares a proof that the tally is correct and provides an interface for voters to see if their receipts are recorded correctly and if their print audited ballots contain consistent confirmation codes with what is recorded.

\subsection{Scantegrity II is Coercion Resistant}

For the purposes of this paper, we will assume that Scantegrity II is a secure voting system. Its security is argued in the Scantegrity papers, while a very thorough proof of its \textit{coercion resistance} property is given by Kusters, Truerung, and Vogt. The definition of coercion resistance is from their earlier paper at CSF 2010. We provide a summary of their main theorem, while omitting many of the details and exact models (see their paper).

Let $P_{\mathsf{Sct}}$ denote the Scantegrity~II protocol, and let
\[
S = P_{\mathsf{Sct}}(k,m,n,\tilde p)
\]
be an election system with the following parameters. $k$ is the number of candidates (excluding abstention), indexed by $i\in\{1,\dots,k\}$. $m$ is the number of dishonest voters whose votes are assumed known to the coercer (static adversary). $n$ is the number of honest voters (excluding one coerced voter). $\tilde p=(p_0,\dots,p_k)$ is the distribution of an honest voter's choice ($p_0$ for abstention, $p_i$ for candidate $i$), with $\sum_{j=0}^k p_j=1$.


Kusters \etal define coercion-resistance roughly as: for any strategy $v$ the coercer forces on the voter, there exists a counter-strategy $\tilde v$ such that (i) the resulting run satisfies the voter's goal $\gamma_i$ with overwhelming probability, while (ii) the coercer cannot distinguish whether the voter obeyed the coercer or used its counter-strategy by more than a security parameter $\delta$. The quantity $\delta=\delta^i_{\min}(n,k,\tilde p)$ is the paper's expression for the best-possible distinguishability advantage available to a coercer in this setting (we refer the interested reader to the paper for its exact details).

\begin{theorem}[Main Result from TK]
Fix $i\in\{1,\dots,k\}$ and let $\delta \;=\; \delta^i_{\min}(n,k,\tilde p).$ Then the Scantegrity~II election system $S=P_{\mathsf{Sct}}(k,m,n,\tilde p)$ is
$\delta$-coercion-resistant with respect to the goal $\gamma_i$.
\end{theorem}


Under this definition, it does not say ``Scantegrity II is coercion resistant'' writ large. Rather it says, ``Scantegrity II is coercion-resistant for specific family of voter goals $\gamma_i$.'' In general, a system may be proven coercion resistant for certain kinds of goals and not for other goals. For the authors' proof of Scantegrity II, they need a specific goal for the proof. The goal they use, $\gamma_i$, can be informally stated as: \textit{if the coercer’s demand is abstention, the voter abstaining is acceptable; otherwise, if the voter casts a vote, it should be for candidate $i$, regardless of which candidate the coercer instructs them to vote for.}


\subsection{Replacing the Switchboard with Eperio} 

As mentioned, the verification back-end in Scantegrity II is referred to as the Switchboard. Eperio was introduced by its authors explicitly as a replacement for the Switchboard. Eperio tables play the same architectural role as the switchboard, while providing proofs that are asserted to be more human-understandable. The paper shows an Eperio proof is simpler to implement (smaller data, less lines of code) than Switchboard proofs and can even be manually checked by a human verifier using a spreadsheet (such as Microsoft Excel) and simple operations.

A blackbox equivalence of Eperio and the Switchboard has not been formally proven. Basin \etal do not seek to prove this, but they do model both Eperio and the Scantegrity switchboard. They show that they operate over the same underlying table structures and for every verification property they prove, they just state the proof would be analogous to Eperio's proof without developing them further. The also show that the same privacy argument applies to both systems. The privacy result they obtain for Eperio, however, comes with two important caveats relative to the Kusters \etal result. First, the notion of privacy is weaker than coercion resistance: it shows that the published verification data does not allow votes to be linked to voters within a table-based model, a property sometimes referred to as receipt freeness, rather than a full game-based coercion-resistance guarantee. Second, their analysis is framed using a simplified Scantegrity-style ballot abstraction rather than the full Scantegrity II ballot format, so the result applies at the level of the switchboard and verification logic, not to the complete human-facing voting protocol.

We state as a conjecture, and without proof, that if the Switchboard is replaced with Eperio, the result from Kuster \etal will continue to hold. We think this is reasonable given the evidence above.

\subsection{Zeeperio is as Coercion Resistant as Eperio}

We now turn to Zeeperio and will start with its coercion resistance. Essentially we will show that whatever a coercer can learn from a Zeeperio transcript, they would already know the same information (perhaps with less assurance) from an Eperio transcript. Therefore whatever level of privacy is achievable by Eperio with Scantegrity-style ballots, the Zeeperio inherits at least the same level. This level is at least receipt-freeness under the definition of Basin \etal and could be coercion resistance under the definition of Kusters \etal if one accepts our conjecture that swapping Scantegrity's Switchboard for Eperio does not reduce privacy in any meaningful way.




\subsection{Zeeperio is as Verifiable as Eperio} 

Basin \etal model Eperio using tables and SP-algebra (selection–projection table algebra) to state verification conditions and prove that these conditions imply integrity (and related) properties through pen-and-paper formal-methods proofs (as opposed to machine-checked verification). In this section, we show the equivalence of Zeeperio's constraints and their model, which we will call the BDGR model or just BDGR. 

The notation we use the main body of our paper and the notation used by BDGR is largely distinct but sometimes a few symbols overlap. Rather than rewriting the BDGR model in our notation, we keep their notation for easier cross-referencing with their paper but we make it easier for the reader to know we are discussing BDGR by placing the main equations in blue boxes, while using pink boxes for Zeeperio.

% Symbols used in the definition of $P_{\mathrm{con}}$.

In BDGR, the election authority reveals a set of Eperio tables but shows only parts of the tables, never the entire table. The entires in the partial table that are unknown are marked with symbol $\bot$. Each artefact $P\in \mathcal{P}_{\mathrm{auth}}$ is in the set of everything published ($\mathcal{P}_{\mathrm{auth}}$). Iterating over each $P$, the model then iterates over every possible $T \in \mathcal{T}_\bot$ from the set of all tables (full or partial). If a table $T$ is consistent with the revealed $P$, which is to say it is the same in possibly permuted order as $P$ with $\bot$ symbols, it is collected. The intersection of all collected tables over each $P$ is denoted $\bigcap_{P\in \mathcal{P}_{\mathrm{auth}}}\{T\in\mathcal{T}_\bot|P\stackrel{\bot}{=}\pi_{\mathrm{sort}(P)}T\}$. 

In their notation, the set of tables that are consistent with the published tally $t$ is denoted $\mathrm{Ind}^{qu}_t(\pi_S\sigma_{M=1})$ which we will not unpack further here, referring the interested reader to their paper. Together, $\mathcal{P}_{\mathrm{con}}$ is a set of full Eperio tables that are consistent with both the tally and the data published in the audit trail. 

\begin{mdframed}[linewidth=0.6pt,backgroundcolor=verylightblue,innerleftmargin=6pt,innerrightmargin=6pt,innertopmargin=4pt,innerbottommargin=4pt]
\[
\footnotesize
\begin{aligned}
\mathcal{P}_{\mathrm{con}}&:=\mathrm{Ind}^{qu}_t(\pi_S\sigma_{M=1}) \cap \bigcap_{P\in \mathcal{P}_{\mathrm{auth}}}\{T\in\mathcal{T}_\bot|P\stackrel{\bot}{=}\pi_{\mathrm{sort}(P)}T\}
\end{aligned}
\]
\end{mdframed}

Everything a voter $v$ sees across an election is specified as their view of the election $R_v$. The collection of all voters' views is defined as Views.

The BDGR model defines an operation $\owedge$ that works like a key-based merge over a set of tables, allowing the input tables to have unknown entries $\bot$. The key Key specifies when two rows should be treated as the same row. The output $\owedge^{Key}(\cdot)$ is the set of possible tables that are consistent merges of the input tables. If the input tables contradict each other, the output set will be empty. Because merges may leave some information underdetermined, $\owedge^{Key}(\cdot)$ will likely contain many tables. The operator $\min$ is then used to extract the least-informative consistent merged tables. Eventually the model will argue that the min , to talk about a single election outcome, BDGR does not require a single merged table; instead it requires that all candidate tables consistent with the evidence yield the same tally.

In an Eperio table, each row has a unique identifier under the key U (and each row corresponds to a specific markable region on a ballot). Using the unique identifier $U$ as a key, the minimum tables of the combined voter views are as follows. 

\begin{mdframed}[linewidth=0.6pt,backgroundcolor=verylightblue,innerleftmargin=6pt,innerrightmargin=6pt,innertopmargin=4pt,innerbottommargin=4pt]
\[
\footnotesize
\begin{aligned}
\mathrm{Views}&:=\{R_v|v\in V\}\\
\bar{V}&:=\min(\owedge^{U}(\mathrm{Views}))\\
\end{aligned}
\]
\end{mdframed}


The BDGR model identifies six predicates $\psi_i$ that should evaluate to true if Eperio is verifiable, sound, and complete, which is the security property $\phi$ they attempt to prove.

\begin{mdframed}[linewidth=0.6pt,backgroundcolor=verylightblue,innerleftmargin=6pt,innerrightmargin=6pt,innertopmargin=4pt,innerbottommargin=4pt]
\begin{definition}[Definition 4]
\label{def:bdgr}
Given a non-empty sort $Key$ of unique keys, $P_{\mathrm{auth}}$, $\mathrm{Views}$, and $P_{\mathrm{con}}$ as in Section~3, let
\[
C = \owedge^{Key}(P_{\mathrm{auth}}\cup \mathrm{Views}) \cap P_{\mathrm{con}}.
\]
We say that an election’s outcome $tal$ corresponds to the voters’ intent, and denote this property by
$\varphi_{Key,tal}(P_{\mathrm{auth}},P_{\mathrm{con}},\mathrm{Views})$, if the following two conditions are satisfied:
\[
(1)\;\; C \neq \emptyset
\qquad\text{and}\qquad
(2)\;\; \forall T \in C,\; \forall T' \in \min(\owedge^{Key}\mathrm{Views}) : tal(T) = tal(T'),
\]
where $tal$ denotes the tally function.
\end{definition}
\end{mdframed}

To relate the BDGR model to Zeeperio's PIOP constraints, we introduce notation that separates two concerns:
(i) the \emph{cryptographic} claim that a verifier acceptance implies the asserted polynomials really vanish (up to negligible error), and
(ii) the \emph{semantic} claim that these vanishing relations faithfully encode Eperio which we will prove via the 6 BDGR predicates.

Let $\mathrm{pub}$ denote the public input to Zeeperio and let $w$ denote the witness. Let $\pi$ denote the PIOP proof transcript (or its non-interactive form), and let $\mathsf{Acc}(\mathrm{pub},\pi)\in\{\mathsf{true},\mathsf{false}\}$ be the verifier’s acceptance predicate.

Zeeperio enforces $\constraints$ algebraic constraints. We write each constraint $c\in\constraints$ as a polynomial identity over a fixed evaluation domain: for every constraint $c$, there is a corresponding \emph{constraint polynomial}: $V_{c}(X;\mathrm{pub},w)$. Intuitively, $V_c$ is constructed so that the constraint $c$ holds exactly when $V_c$ evaluates to $0$ on every point of the domain (or vanishes). If w let $H$ be the evaluation domain, we can define the vanishing predicate as: $\mathsf{Vanish}(f)\;:\Leftrightarrow\;\forall x\in H:\; f(x)=0$. $\mathsf{Acc}(\mathrm{pub},\pi)$ is the event that the verifier accepts the proof, while $\mathsf{Vanish}$ is the underlying mathematical statement that the claimed polynomials vanish on $H$.

We now state the standard soundness guarantee for polynomial IOPs. There exists a soundness error bound $\epsilon$ such that:
\[
\mathsf{Acc}(\mathrm{pub},\pi)\Rightarrow_{\epsilon}\exists w:\bigwedge_j \mathsf{Vanish}\!\left(V_{c_j}(X;\mathrm{pub},w)\right).
\]
In words, except with probability at most $\epsilon$, an accepted proof implies the existence of a witness $w$ for which all constraint polynomials vanish on $H$. Proof of this can be found in the Plonk paper~\cite{GWC19}, which also uses vanishing polynomials to prove knowledge of values that satisfy any arithmetic circuit (and this can be transformed into a general purpose SNARK). While Zeeperio could be defined as a circuit and turned into a SNARK through Plonk, it is more efficient to define custom vanishing polynomials for Eperio directly, creating a special purpose SNARK. 

Next we turn our attention to showing that satisfying the Zeeperio constraints is strong enough to imply the BDGR verification predicates:
\[
\exists w:\bigwedge_j \mathsf{Vanish}\!\left(V_{c_j}(X;\mathrm{pub},w)\right)\Rightarrow \bigwedge_i \psi_i(\mathcal{P}_{\mathrm{auth}},P_{\mathrm{con}},\mathrm{Views}).
\]
This implication is not cryptographic; it is a semantic correspondence argument. Concretely, we interpret each witness polynomial as a column of an underlying table (via evaluation on $H$), and prove that each vanishing constraint enforces the corresponding BDGR table property (e.g., inclusion, uniqueness, tally consistency, and no-stuffing), thereby establishing each $\psi_i$.

\subsection{Aikam see here}

% NOTE: use \owedge for the combine operator (as you already do).
% Here we write it consistently with a superscript key, and as a function \owedge^{Key}(\cdot).

% assuming you defined:
% \newcommand{\BDGR}[1]{...}

\BDGR{\psi_{0}&:=\owedge^{\{U\}}(\mathcal{P}_{\mathrm{auth}})\cap\bigcap_{P\in\mathcal{P}_{\mathrm{auth}}}\mathrm{shape}_{P}\neq\emptyset}

\textblue{Argue that Zeeperio's constraints satisfy this property.}

\BDGR{\psi_{1}&:=\bigwedge_{v\in V}\bigwedge_{P\in\mathcal{P}_{\mathrm{auth}}}\bigl(\pi_{U,M}R_v\subseteq^{\#}\pi_{U,M}P\bigr)}

\textblue{Argue that Zeeperio's constraints satisfy this property.}

\BDGR{\psi_{\mathrm{print\text{-}audit}}&:=\owedge^{\{U\}}\bigl(\{\pi_{U,S}(R)\mid R\in\mathrm{Views}\}\bigr)\cap\owedge^{\{U\}}(\mathcal{P}_{\mathrm{auth}})\cap\bigcap_{P\in\mathcal{P}_{\mathrm{auth}}}\mathrm{shape}_{P}\neq\emptyset}

\textblue{Argue that Zeeperio's constraints satisfy this property.}

\BDGR{\psi_{\mathrm{tally}}&:=t\in\bigcap_{P\in\mathcal{P}_{\mathrm{auth}}}\mathrm{Ind}^{qu}_{P}\bigl(\{\pi_{S}\sigma_{M=1}\}\bigr)}

\textblue{Argue that Zeeperio's constraints satisfy this property.}

\BDGR{\psi_{\mathrm{unique}}&:=\owedge^{\{U\}}\bigl(\{\pi_{V,U}R\mid R\in\mathrm{Views}\}\bigr)\neq\emptyset}

\textblue{Argue that Zeeperio's constraints satisfy this property.}

\BDGR{\psi_{\mathrm{no\text{-}stuffing}}&:=\forall P\in\mathcal{P}_{\mathrm{auth}}:\#\sigma_{M=1}\pi_{M}P=\#\sigma_{M=1}\pi_{M}V}

\textblue{Argue that Zeeperio's constraints satisfy this property.}

\vanishP{
\Bigl(\bigwedge_j \mathsf{Acc}(\mathrm{pub},\pi)&\Rightarrow \Bigl(\bigwedge_i \psi_i\Bigr)\\
\psi_{0}\wedge\psi_{1}\wedge\psi_{\mathrm{tally}}\wedge\psi_{\mathrm{print\text{-}audit}}\wedge\psi_{\mathrm{unique}}\wedge\psi_{\mathrm{no\text{-}stuffing}}&\Rightarrow\varphi
}

We prove Zeeperio's constraints imply Basin's predicates. Basin \etal prove that if these predicates hold, then the security definition $\phi$ which is provided as Definition~\ref{def:bdgr} above, is satisfied. \qed

\section{Security of Zeeperio via Basin et al.'s table-based soundness theorem}

\subsection{Basin et al.'s integrity property and the fixed-Eperio soundness theorem}

We work in the table framework of Basin et al.
An election is represented by multisets of tuples ("tables") possibly containing
unknown placeholder values~$\bot$; joins and consistency are expressed using
the merge operator $\owedge^{\mathrm{Key}}$ under a designated unique key sort~$\mathrm{Key}$.

\paragraph{Eperio election table and tally query.}
In Basin et al.'s formalization of \emph{Eperio}, the (secret) election table has sort
$\{U,M,S\}$, where $U$ is the ballot-position identifier (serial number together with an
in-ballot position), $S$ is a candidate/selection label, and
$M\in\{1,0,-1\}$ denotes \emph{marked}, \emph{unmarked}, and \emph{print-audit}, respectively. 
The tally is the SP-query
\[
\mathrm{tal} \;:=\; \pi_S \sigma_{M=1},
\]
which means: select marked entries and project to the candidate column~$S$.

\paragraph{Global integrity property.}
Let $P_{\mathrm{auth}}$ be the tables published by the election authority,
$P_{\mathrm{con}}$ be the set of tables satisfying public protocol constraints (including the announced tally),
and $Views=\{R_v\mid v\in V\}$ be the collection of voters' view tables.
For a nonempty key sort $\mathrm{Key}$, Basin et al.\ define
\[
C \;:=\; \owedge^{\mathrm{Key}}\bigl(P_{\mathrm{auth}}\cup Views\bigr)\ \cap\ P_{\mathrm{con}}.
\]
The integrity property $\phi_{\mathrm{Key},\mathrm{tal}}(P_{\mathrm{auth}},P_{\mathrm{con}},Views)$ holds iff
(i) $C\neq\emptyset$, and (ii) every completion $T\in C$ yields the same tally as every
minimal completion of the voters' combined view:
\[
\forall T\in C,\ \forall T'\in \min\bigl(\owedge^{\mathrm{Key}}Views\bigr):\quad
\mathrm{tal}(T)=\mathrm{tal}(T').
\]
This is Basin et al.'s Definition~4:
\emph{all mutually consistent explanations of the published data and the voters' views
satisfy the announced constraints and induce the same outcome as the voters' intent}.

\paragraph{Local checks and soundness for Eperio.}
Basin et al.\ decompose $\phi$ into locally checkable properties ("checks")~$\psi_i$
that correspond to the protocol's verification steps.
For Eperio, the checks include:
\begin{align*}
\psi_0 \ &:=\ \owedge^{\{U\}}P_{\mathrm{auth}}\ \cap\ \bigcap_{P\in P_{\mathrm{auth}}}\mathrm{shape}_P \ \neq\ \emptyset,\\
\psi_1 \ &:=\ \bigwedge_{v\in V}\ \bigwedge_{P\in P_{\mathrm{auth}}}\Bigl(\pi_{U,M}R_v\ \subseteq_{\#}\ \pi_{U,M}P\Bigr),\\
\psi_{\mathrm{tally}} \ &:=\ t\ \in\ \bigcap_{P\in P_{\mathrm{auth}}}\mathrm{Ind}^{\mathrm{qu}}_{P}\bigl(\{\pi_S\sigma_{M=1}\}\bigr),\\
\psi_{\mathrm{print\text{-}audit}} \ &:=\
\owedge^{\{U\}}\{\pi_{U,S}(R)\mid R\in Views\}\ \cap\ \owedge^{\{U\}}P_{\mathrm{auth}}\ \cap\
\bigcap_{P\in P_{\mathrm{auth}}}\mathrm{shape}_P\ \neq\ \emptyset,
\end{align*}
and Basin et al.\ additionally identify two \emph{missing} checks needed for soundness:
\begin{align*}
\psi_{\mathrm{unique}} \ &:=\ \owedge^{\{U\}}\{\pi_{V,U}R \mid R\in Views\}\ \neq\ \emptyset,\\
\psi_{\mathrm{no\text{-}stuffing}} \ &:=\
\forall P\in P_{\mathrm{auth}}:\ \#\sigma_{M=1}\pi_M P\ =\ \#\sigma_{M=1}\pi_M V,
\quad\text{where }V=\min\bigl(\owedge^{\{U\}}Views\bigr).
\end{align*}
With these additions, they show that the verification procedure is sound in their possibilistic model:
\[
\psi_0\wedge\psi_1\wedge\psi_{\mathrm{tally}}\wedge\psi_{\mathrm{print\text{-}audit}}
\wedge\psi_{\mathrm{unique}}\wedge\psi_{\mathrm{no\text{-}stuffing}}
\ \Longrightarrow\ \phi_{\{U\},\pi_S\sigma_{M=1}}.
\]
This implication is stated in the Basin paper and proved in their appendix.

\subsection{Zeeperio commitments, proof soundness, and induced Eperio table}
\label{sec:zeeeperio-model}

Fix template parameters $B$ ballots and $C$ candidate positions per ballot, and let $P:=BC$.
Let $n\ge P$ be a power of two and let $H=\{\omega^0,\dots,\omega^{n-1}\}\subset\mathbb{F}_q$
be a multiplicative subgroup of size~$n$.

Zeeperio commits to witness polynomials $Code(X),Audit(X),Mark(X)$ whose evaluations on~$H$
encode table columns, padded with zeros on indices $i\ge P$.
Write $Code_i:=Code(\omega^i)$, $Audit_i:=Audit(\omega^i)$, and $Mark_i:=Mark(\omega^i)$.

\paragraph{Cryptographic soundness model.}
Let $\Pi_{\mathrm{main}}$ denote the Zeeperio election proof, and let $\Pi_{\mathrm{receipt}}$ and
$\Pi_{\mathrm{audit}}$ denote the voter-facing proofs for receipt checking and print-audit openings.
We rely on standard properties of pairing-based polynomial commitments and SNARKs:
\begin{enumerate}
\item[(A1)] \textbf{PCS binding.} The polynomial commitment scheme used by Zeeperio is computationally binding.
For KZG commitments this follows from standard pairing assumptions.
\item[(A2)] \textbf{Knowledge soundness.} If the verifier (smart contract) accepts a Zeeperio proof,
then there exists a witness assignment (in particular, the committed polynomials and auxiliary polynomials)
satisfying all enforced polynomial identities on~$H$, except with negligible probability.
For Fiat-Shamir transformed PIOP/SNARK systems this is the standard soundness/extractability
guarantee in the random-oracle model.
\end{enumerate}

\paragraph{Public key and candidate columns.}
Since Zeeperio does not shuffle rows, the ballot identifier and in-ballot position are public.
For each $i\in\{0,\dots,P-1\}$ define
\[
b(i):=\left\lfloor i/C\right\rfloor,\qquad k(i):= i\bmod C,\qquad
U(i):=(b(i),k(i)).
\]
Let $S(k)$ be the publicly known candidate label at position~$k$ in the ballot template
(with $k\in\{0,\dots,C-1\}$), and write $S(i):=S(k(i))$.

\paragraph{Induced Eperio-style mark column and table.}
Define an Eperio-style entry $M(i)\in\{-1,0,1\}$ by
\[
M(i)\;:=\;
\begin{cases}
-1 & \text{if }Audit_i=1,\\
1  & \text{if }Audit_i=0 \text{ and }Mark_i=1,\\
0  & \text{if }Audit_i=0 \text{ and }Mark_i=0.
\end{cases}
\]
The induced known election table is
\[
E^{Z}:=\{\langle U:U(i),\,M:M(i),\,S:S(i)\rangle \mid i\in\{0,\dots,P-1\}\}.
\]

\subsection{Zeeperio constraints imply Eperio well-formedness and tally correctness}
\label{sec:constraint-lemmas}

Throughout this subsection, assume that the on-chain verifier accepts $\Pi_{\mathrm{main}}$.
By (A2), there exist witness polynomials satisfying all enforced Zeeperio polynomial identities on~$H$.

\begin{lemma}[Bitness and padding]
\label{lem:bitness-padding}
For all $i\ge P$, $Audit_i=0$ and $Mark_i=0$. For all $i<P$, $Audit_i,Mark_i\in\{0,1\}$.
\end{lemma}
\begin{proof}
Constraint c1.1 enforces $Audit_i=0$ on padding indices and c1.2 enforces $Audit_i\in\{0,1\}$ on~$H$.
Likewise, c2.1 enforces $Mark_i=0$ on padding indices and c2.2 enforces $Mark_i\in\{0,1\}$ on~$H$.
\end{proof}

\begin{lemma}[Whole-ballot audit blocks]
\label{lem:audit-blocks}
For each ballot $b\in\{0,\dots,B-1\}$ and its block $I_b:=\{bC,\dots,bC+C-1\}$,
either $Audit_i=1$ for all $i\in I_b$ or $Audit_i=0$ for all $i\in I_b$.
\end{lemma}
\begin{proof}
Constraint c1.3 enforces that the block-sum of $Audit$ at each ballot start is either $0$ or $C$.
By Lemma~\ref{lem:bitness-padding}, $Audit_i\in\{0,1\}$ on $I_b$, so the sum is $C$ iff all entries are~$1$
and is $0$ iff all entries are~$0$.
\end{proof}

\begin{lemma}[At most one mark per ballot]
\label{lem:no-overvote}
For each ballot block $I_b$, $\sum_{i\in I_b} Mark_i \in \{0,1\}$.
\end{lemma}
\begin{proof}
Constraint c2.3 enforces that the block-sum of $Mark$ at each ballot start is either $0$ or $1$.
Since $Mark_i\in\{0,1\}$ by Lemma~\ref{lem:bitness-padding}, this is exactly the stated claim.
\end{proof}

\begin{lemma}[Audit and mark are disjoint]
\label{lem:disjoint-audit-mark}
For all $i<P$, $Audit_i\cdot Mark_i=0$. Hence $M(i)$ is well-defined and belongs to $\{-1,0,1\}$.
\end{lemma}
\begin{proof}
Constraint c3.1 enforces $Audit(X)Mark(X)$ vanishes on $H$, i.e., $Audit_i Mark_i=0$ for each $i$.
Together with Lemma~\ref{lem:bitness-padding}, this implies the cases in the definition of $M(i)$
are disjoint.
\end{proof}

\begin{lemma}[Ballot-level well-formedness of $M$]
\label{lem:M-wellformed}
For each ballot block $I_b$, exactly one of the following holds:
\begin{enumerate}
\item[(i)] (\emph{print-audit}) $M(i)=-1$ for all $i\in I_b$;
\item[(ii)] (\emph{cast}) there exists a unique $i^\star\in I_b$ with $M(i^\star)=1$ and $M(i)=0$ for all $i\in I_b\setminus\{i^\star\}$;
\item[(iii)] (\emph{unused}) $M(i)=0$ for all $i\in I_b$.
\end{enumerate}
\end{lemma}
\begin{proof}
By Lemma~\ref{lem:audit-blocks}, either $Audit$ is all-ones or all-zeros on $I_b$.
If it is all-ones, then by Lemma~\ref{lem:disjoint-audit-mark} we have $Mark_i=0$ for all $i\in I_b$,
so $M(i)=-1$ throughout the block.
If $Audit$ is all-zeros, then $M(i)=Mark_i$ for all $i\in I_b$, and Lemma~\ref{lem:no-overvote}
yields either exactly one $1$ in the block, or all zeros.
\end{proof}

\begin{lemma}[Tally correctness]
\label{lem:tally-correct}
Let $t$ be the announced tally table of sort $S$ where the candidate label $S(j)$
appears with multiplicity $Tally[j]$ for each $j\in\{0,\dots,C-1\}$.
Then $\mathrm{tal}(E^{Z}) = t$.
\end{lemma}
\begin{proof}
By Lemma~\ref{lem:disjoint-audit-mark}, rows with $M(i)=1$ are exactly those with $Mark_i=1$.
For a fixed position $j\in\{0,\dots,C-1\}$, the rows with $S(i)=S(j)$ are precisely the indices
$i\equiv j\pmod C$. Zeeperio's strided accumulator $Acc_{\mathrm{Vote}}$ sums $Mark$ over exactly these
indices, and constraint c4.3 enforces $Acc_{\mathrm{Vote}}(\omega^j)=Tally[j]$ for each $j$.
Since padding indices $i\ge P$ contribute zero by Lemma~\ref{lem:bitness-padding},
the multiplicity of $S(j)$ in $\pi_S\sigma_{M=1}(E^{Z})$ equals $Tally[j]$ for all $j$, hence
$\mathrm{tal}(E^{Z})=t$.
\end{proof}

\subsection{Realizing Basin's checks with Zeeperio verification}
\label{sec:basin-checks-hold}

We now instantiate Basin's objects $(P_{\mathrm{auth}},P_{\mathrm{con}},Views)$ from a Zeeperio execution.

\paragraph{Virtual publication tables.}
Define Eperio-style partial publication tables (with missing values~$\bot$) by
\[
P^{UM}\ :=\ \{\langle U:U(i),\,M:M(i),\,S:\bot\rangle \mid 0\le i<P\},
\qquad
P^{MS}\ :=\ \{\langle U:\bot,\,M:M(i),\,S:S(i)\rangle \mid 0\le i<P\},
\]
and set $P_{\mathrm{auth}}^{Z}:=\{P^{UM},P^{MS}\}$.

Let $P_{\mathrm{con}}^{Z}$ be Basin et al.'s Eperio constraint set instantiated for the announced tally~$t$
and the public template shape \cite[\S3.3]{BasinEtAl2021Tables}.

\paragraph{Voter views and on-chain validation.}
For each voter $v$, let $R_v$ be the table describing the view that $v$ accepts after running
Zeeperio's voter-facing verification (receipt check for cast ballots, print-audit check for audited ballots).
We define $Views^{Z}:=\{R_v\mid v\in V\}$ and require as part of Zeeperio’s verification procedure that:
(i) each $R_v$ is accompanied by a proof $\Pi_v\in\{\Pi_{\mathrm{receipt}},\Pi_{\mathrm{audit}}\}$ that is verified
against the same commitments as $\Pi_{\mathrm{main}}$, and
(ii) the smart contract rejects duplicate ballot identifiers in voter submissions (so the set $Views^{Z}$ is key-consistent).

\begin{lemma}[Zeeperio implies $\psi_0$ and $\psi_{\mathrm{tally}}$]
\label{lem:psi0-psitally}
If $\Pi_{\mathrm{main}}$ verifies, then $\psi_0(P_{\mathrm{auth}}^{Z})$ and
$\psi_{\mathrm{tally}}(P_{\mathrm{auth}}^{Z},t)$ hold.
\end{lemma}
\begin{proof}
Both $P^{UM}$ and $P^{MS}$ are projections of the same known table $E^{Z}$ with $\bot$-filled columns,
so they have compatible shapes and merge consistently under the key~$U$. This is exactly $\psi_0$.
For $\psi_{\mathrm{tally}}$, Lemma~\ref{lem:tally-correct} shows that the query $\pi_S\sigma_{M=1}$ applied to
$E^{Z}$ yields $t$, hence $t$ is uniquely determined by the $\{M,S\}$-view and therefore lies in
$\mathrm{Ind}^{\mathrm{qu}}_{P}(\{\pi_S\sigma_{M=1}\})$ for each $P\in P_{\mathrm{auth}}^{Z}$.
\end{proof}

\begin{lemma}[Zeeperio voter proofs imply $\psi_1$ and $\psi_{\mathrm{print\text{-}audit}}$]
\label{lem:psi1-psiprint}
Assume $\Pi_{\mathrm{main}}$ verifies and that each voter-facing proof $\Pi_v$ verifies against the same commitments.
Then $\psi_1(P_{\mathrm{auth}}^{Z},Views^{Z})$ and $\psi_{\mathrm{print\text{-}audit}}(P_{\mathrm{auth}}^{Z},Views^{Z})$ hold.
\end{lemma}
\begin{proof}
By (A1) and (A2), acceptance of a voter-facing proof $\Pi_v$ implies that the tuple(s) recorded in $R_v$
match the unique witness table $E^{Z}$ on the columns they claim (openings cannot be consistent with two different
tables). Therefore $\pi_{U,M}R_v\subseteq_{\#}\pi_{U,M}E^{Z}=\pi_{U,M}P^{UM}$ for each voter, yielding~$\psi_1$.
The same binding argument for print-audit proofs implies that the $\{U,S\}$-subtables contributed by audited ballots
are merge-consistent with $P_{\mathrm{auth}}^{Z}$ (and preserve the published shape), which is exactly
$\psi_{\mathrm{print\text{-}audit}}$.
\end{proof}

\begin{lemma}[Uniqueness and no-stuffing are enforced in Zeeperio]
\label{lem:unique-nostuff}
Let $\mathsf{Cast}\subseteq\{0,\dots,B-1\}$ be the public set of ballot identifiers for which a \emph{cast-ballot}
receipt check has been accepted by the smart contract (equivalently, there exists a verified proof $\Pi_{\mathrm{receipt}}$
for that ballot). Assume the contract enforces that each ballot identifier can be accepted at most once, i.e., $\mathsf{Cast}$
is a set. Let $N_{\mathrm{cast}}:=|\mathsf{Cast}|$ and let the contract supply the value $Sum_{\mathrm{Mark}}:=N_{\mathrm{cast}}$
as a public input to $\Pi_{\mathrm{main}}$. Then $\psi_{\mathrm{unique}}(Views^{Z})$ and
$\psi_{\mathrm{no\text{-}stuffing}}(P_{\mathrm{auth}}^{Z},Views^{Z})$ hold.
\end{lemma}
\begin{proof}
(\emph{Uniqueness}.) Since each accepted voter view table $R_v\in Views^{Z}$ is tied to a ballot identifier $b$
appearing in its $U$-column (via $U(i)=(b,k)$ for positions $k$), and the contract rejects duplicate ballot identifiers,
no two tables in $\{\pi_{V,U}R\mid R\in Views^{Z}\}$ assign conflicting $V$-values to the same key~$U$.
Hence $?_{\{U\}}\{\pi_{V,U}R\mid R\in Views^{Z}\}\neq\emptyset$, i.e.\ $\psi_{\mathrm{unique}}$ holds.

(\emph{No-stuffing}.) By Lemma~\ref{lem:disjoint-audit-mark}, the $M=1$ rows in $P^{UM}$ correspond exactly to the
$Mark_i=1$ entries in the witness, so $\#\sigma_{M=1}\pi_M P^{UM}=\sum_{i=0}^{P-1} Mark_i$.
Constraint c2.6 enforces $\sum_{i=0}^{P-1} Mark_i = Sum_{\mathrm{Mark}} = N_{\mathrm{cast}}$.
On the other hand, for $V=\min(?_{\{U\}}Views^{Z})$, each $b\in\mathsf{Cast}$ contributes (by receipt-check soundness)
a row with $M=1$ to $V$, and by Lemma~\ref{lem:no-overvote} no ballot contributes more than one such row.
Therefore $\#\sigma_{M=1}\pi_M V = |\mathsf{Cast}| = N_{\mathrm{cast}}$, yielding $\psi_{\mathrm{no\text{-}stuffing}}$.
\end{proof}

\subsection{Main inheritance theorem}
\label{sec:inheritance-theorem}

\begin{theorem}[Zeeperio inherits Basin et al.'s global integrity property]
\label{thm:zeeperio-inherits}
Assume (A1)--(A2). If $\Pi_{\mathrm{main}}$ verifies and all voter-facing proofs verify as specified above, then
\[
\phi_{\{U\},\pi_S\sigma_{M=1}}(P_{\mathrm{auth}}^{Z},P_{\mathrm{con}}^{Z},Views^{Z})
\]
holds.
\end{theorem}
\begin{proof}
By Lemma~\ref{lem:psi0-psitally} we have $\psi_0$ and $\psi_{\mathrm{tally}}$.
By Lemma~\ref{lem:psi1-psiprint} we have $\psi_1$ and $\psi_{\mathrm{print\text{-}audit}}$.
By Lemma~\ref{lem:unique-nostuff} we have $\psi_{\mathrm{unique}}$ and $\psi_{\mathrm{no\text{-}stuffing}}$.
Therefore the premises of Basin et al.'s Eperio soundness implication are satisfied, yielding the desired $\phi$.
\end{proof}

\clearpage{Security Proof}

